### 2013-12-27 BeamPaper.tex
First commit

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{color}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{import}
\usepackage[section]{placeins}

\usepackage{cleveref}
\usepackage{autonum}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\graphicspath{ {../} }
\graphicspath{ {./images/} }
\newcommand{\diagrampath}{./diagrams/}
\newcommand{\plotpath}{./plots}

\newcommand{\mathbi}[1]{\mathit{\mathbf{#1}}}

\newcommand\vstate[3]{%
	\mathbf{\underline{#1}}%
	\ifstrempty{#2}{}{[#2]}%
	\ifstrempty{#3}{}{\langle #3 \rangle}}
\newcommand\sstate[3]{%
	\mathit{\underline{#1}}%
	\ifstrempty{#2}{}{[#2]}%
	\ifstrempty{#3}{}{\langle #3 \rangle}%
	}

\title{Peridynamic Beams: \\ A Non-ordinary, State Based Model}
\author{James O'Grady \and John T. Foster}
%\date{}                                           % Activate to display a given date or no date

\begin{document}

\begin{abstract}
This paper develops a new peridynamic state based model to represent the bending of an Euler-Bernoulli beam.
This model is non-ordinary and derived from the concept of a rotational spring between bonds.
While multiple peridynamic material models capture the behavior of solid materials, this is the first 1D state based peridynamic model to resist bending.
For sufficiently homogenous and differentiable displacements, the model is shown to be equivalent to Eringen's nonlocal elasticity.
As the peridynamic horizon approaches 0, it reduces to the classical Euler-Bernoulli beam equations.
Simple test cases demonstrate the model's performance.
\end{abstract}

\maketitle

\section{Introduction}
The final goal of many mechanical engineering analyses is the prediction and description of material failure.
When processes such as fracture are modeled, the differential equations of classical mechanics are ill-defined at the resulting discontinuities.
A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement, so that discontinuities evolve naturally and require no special treatment.
Various peridynamic models capture the material behavior of 3-dimensional solid objects, but would be very expensive to implement for a thin plate or beam.
Other peridynamic models capture tension and compression in 1D bars and 2D plates, but these models do not resist transverse displacement.
A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.

This paper begins to remedy that lack in the simplest case by presenting a peridynamic equivalent to an Euler-Bernoulli beam.
In addition to directly modeling a thin beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
Because many analyses of interest are partly or wholly comprised of these types of features, their development is an important addition to the capabilities of peridynamic analysis.

The second section of this paper provides a brief introduction to peridynamics, including state based models.
The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
The fourth section compares the model to Eringen's nonlocal elasticity for small peridynamic horizons.
The fifth section demonstrates the beam model with simple test cases.
%
\section{Peridynamics}
\label{sec:PDintro}
The term \textit{peridynamic} was coined by Silling in \cite{silling2000reformulation} and alludes to the fact that the force at a point is affected by nearby material configuration.
Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
These higher-order derivatives impose greater stronger continuity requirements than the classical model. 
By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation 
%
\begin{equation}
\label{eq:PDCoPV}
\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x})
\end{equation}
%
rather than the classical \textit{differential} equation.
Instead of the divergence of stress, we have the integral of a ``force" function $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$. 
This force function may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
While the simplest force functions recreate a one-parameter linear elastic solid material\cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors\cite{silling2005peridynamic}.
To describe force functions that incorporate the behavior of all points in the nearby material (not just \(\mathbf{x}\) and \(\mathbf{q}\)), we must introduce the concept of a peridynamic state.

Introduced by Silling et al. in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
The most common states are scalar states and vector states which are scalar and vector valued, respectively.
Unlike multiplication by a second order tensor, which can only map vectors linearly to other vectors, vector states can produce highly nonlinear or even discontinuous mappings.
Important properties of states are magnitude and direction, while important operations include the addition and decomposition of states, inner and tensor products, and the Fr\'{e}chet derivative of a function with respect to a state~\cite{silling2007peridynamic}.

Conservation of linear momentum in the \textit{state based} peridynamic formulation results in the equation of motion,
%
\begin{equation}
\label{eq:PDstateEoM}
\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),
\end{equation}
%
in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
The deformed image of the vector $\mathbf{q}-\mathbf{x}$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation}. 
%
\begin{equation}
\label{eq:PDdeformation}
\vstate{Y}{\mathbf{x}}{\mathbf{q}-\mathbf{x}} = (\mathbf{q}-\mathbf{x}) + (\mathbf{u}(\mathbf{q})-\mathbf{u}(\mathbf{x}))
\end{equation}
%

Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.
If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  
Models in which they are not in the same direction are called \textit{non-ordinary}.
Silling et al. demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
Foster et al. \cite{foster2010viscoplasticity} and Warren et. al. \cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
%
\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{simpleBondPair.eps_tex}
\caption{Illustration of a bond pair model that resists angular deformation}
\label{fig:SimpleBondpair}
\end{figure}
%
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \( w = \alpha [1 + \cos(\theta) ] \), we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic}.
%
\begin{equation}
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} =\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
\end{equation}
%
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}. 
The force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{bondPair.eps_tex}
\caption{Deformation and force vector states}
\label{fig:Bondpair}
\end{figure}
%
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small. 
Because the potential energy and force states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}. 
Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.
\subsection{Energy Equivalence}
%
We will begin with the assumptions from Euler beam theory: length much greater than thickness, small displacements, and small rotations. 
The latter two assumptions allow us to simplify our equations. 
%
\begin{equation}
\label{eq:beam}
\theta(\vstate{Y}{}{\xi})\approx \sin(\theta(\vstate{Y}{}{\xi})) = \frac{(\vstate{Y}{}{\xi})_y}{|\vstate{Y}{}{\xi}|} \approx \frac{y(x+\xi)-y(x)}{\xi}
\end{equation}
%
\begin{equation}
\label{eq:beamdtheta}
\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}
\end{equation}
%
Using a second order Taylor series to approximate $y$ around $x$, this last term in \cref{eq:beamdtheta} becomes a function of the second derivative of displacement, which we will call \(\kappa\).
%
\begin{equation}
\label{eq:beamdtheta2}
\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi \kappa+\mathcal{O}(\xi^3) 
\end{equation}
%
and if the curvatures are also small enough,
%
\begin{align}
\label{eq:continuousBeamw}
w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \alpha\frac{\xi^2}{2}\kappa^2 +\mathcal{O}(\xi^4) .
\end{align}
%
If we use a weighting function \(\omega(\xi)=\omega(|\xi|)\), the resulting strain energy density for the continuous peridynamic beam is
%
\begin{equation}
W \approx \int_{-\delta}^\delta \omega(\xi)\alpha\left(\frac{\xi^2}{2}\kappa^2 +\mathcal{O}(\xi^4)\right) d\xi = \frac{\alpha}{2}\left(\kappa^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 d\xi +\int_{-\delta}^\delta \omega(\xi)\mathcal{O}(\xi^4)d\xi\right) .
\end{equation}
%
By choosing \(\alpha\) corresponding to our choices of weighting function, peridynamic horizon, and beam geometric and material properties, we can ensure that the potential energy density associated with a well-behaved deformation matches the prediction of Euler beam theory.
%
\begin{align}
\label{eq:classicbeam}
\alpha = \frac{c}{m} ;\; c= EI ;\; m=\int_{-\delta}^\delta \omega(\xi)\xi^2 d\xi \implies W=\frac{EI}{2}\kappa^2+\mathcal{O}(\delta^2)
\end{align}
%

\subsection{Weighting Function and Perfect Plasticity}
The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
Consider an Euler beam in bending with curvature \(\kappa\). 
Fibers running parallel to the neutral axis of the beam are stretched in proportion to their distance from the neutral axis, with strain \(\epsilon = y\kappa\). 
If the fibers are linearly elastic, then the axial stress at each location is \(\sigma = E\epsilon = Ey\kappa\), and the contribution to supported moment \(dM = \kappa E y^2 dA\). 
By comparing the formulations for the moments carried by the Euler beam in \cref{fig:EulerBending} and those of the bond-pair beam in \cref{fig:BPBending}, we see some definite parallels.
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{EulerBending.eps_tex}
\caption{Euler beam moment contribution}
\label{fig:EulerBending}
\end{figure}
%%
\begin{figure}[h]
\subinputfrom{\diagrampath}{BondPairBending.eps_tex}
\caption{Bond-pair moment contribution}
\label{fig:BPBending}
\end{figure}
%
\begin{align}
M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy \\
%
M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi
\end{align}
%
The term \(y\) is the distance from the beam's neutral axis and \(b(y)\) is the width of the beam at that distance from the neutral axis. 
The similarity between classical and peridynamic moment formulations suggests a possible formulation for the weighting function:
%
\begin{equation}
\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}
\end{equation}
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{WeightProfile.eps_tex}
\caption{A cross-section dependent weight function}
\label{fig:WeightProfile}
\end{figure}
%
This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
An example is shown in \cref{fig:WeightProfile}.
While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.

In a bent Elastic Perfectly Plastic beam, axial fibers are still stretched in proportion to their distance from the neutral axis, but the relationship \(\sigma = E\epsilon = Ey\kappa\) only holds for \(|\epsilon| = |y\kappa| < \epsilon_c\). 
For greater stretches, the relationship becomes \(\sigma = \pm E\epsilon_c \). 
To model this behavior, consider a bond pair with similar behavior: for angular deformation less than some critical angle, the model behaves as previously described, but the magnitude of the force remains constant above a critical deformation
%
\[ 
|\vstate{T}{}{\xi}| = 
  \begin{cases}
    \alpha \frac{\sin(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}))}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta < \theta_c\\
    \alpha \frac{\sin(\theta_c)}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta \geq \theta_c\
  \end{cases}
\]
%
to determine the critical angle \(\theta_c\), we let the onset of plasticity in pairs of the longest bonds to coincide with the onset of plasticity in the fibers at the top and bottom surfaces of the classical beam. 
For small curvatures \(\Delta\theta = \xi\kappa\implies\Delta\theta_c = \frac{2\delta\epsilon_c}{t}\). 
For curvatures \(|\kappa| > \kappa_c=\frac{2\epsilon_c}{t}\), the radius within which bonds are in the elastic region is \(\delta_e = \delta \frac{\kappa_c}{\kappa}\), and parallels the distance from the beam centerline that fibers are in the elastic region \(y_e = \frac{t}{2} \frac{\kappa_c}{\kappa}\)
%
\begin{align}
  M_\text{classical} &= 2 \int_{0}^{y_e}E b(y)y^2 \kappa dy +2 \int_{y_e}^{\frac{t}{2}}E b(y) \epsilon_c y dy \\
  M_\text{PD} &= 2 \int_{0}^{\delta_e}\alpha \omega(\xi) \xi^2 \kappa d\xi +2 \int_{\delta_e}^{\delta}\alpha \omega(\xi) \Delta\theta_c \xi d\xi 
\end{align}
%
Of course, as long as the force is independent of history, this model only represents a nonlinear elastic material. 
By keeping track of the plastic deformation \(\theta^p (\xi) = \theta-\theta_c\) of each bond-pair, and applying it as an offset, we can reproduce the hysteresis associated with elastic-perfectly-plastic deformation.
%
%
\section{Relation to Eringen Nonlocality}
%If we relax our homogeneity assumption somewhat, we recover from \cref{eq:beamdtheta} slightly more complex expressions for change in angle
If we keep an additional term from the Taylor series approximation of \cref{eq:beamdtheta}, we recover a slightly more complex expressions for change in angle
%
\begin{equation}
\label{eq:beamdtheta2}
\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)=  \pi-\xi \kappa-\frac{\xi^3}{12} \kappa''+\mathcal{O}(\xi^5)
\end{equation}
%
and for the strain energy
%
%\begin{equation}
%W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{3\; \xi^4}{8}\kappa^4+\mathcal{O}(\xi^6)) d\xi .
%\end{equation}
%
%
\begin{equation}
W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{\xi^4}{24}\kappa^4+\mathcal{O}(\xi^6)) d\xi .
\end{equation}
%
As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
We can picture a nonlocal modulus based on the nonlocal curvature \(\bar{\kappa}= (\kappa + \frac{\xi^2}{12}\kappa'')\), so that 
%
\begin{equation}
W \approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .
\end{equation}
%  
This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
The same analysis can be taken further to obtain higher-order energy terms with even powers of \(\xi\) and even order derivatives of \(\kappa\). 
Not all of these higher-order terms can be separated into the product of a local curvature and nonlocal modulus.

\section{Numerical Simulation}
\subsection{Discretized Model}
For analysis purposes, it is often useful to represent a continuum part with a discrete version. 
Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
%
\begin{align}
\label{eq:discreteBeamw}
w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}\right)^2
\end{align}
%
\begin{align}
\label{eq:discretebeam}
\alpha &= \frac{c\; \Delta x}{m} ;\; c= EI ;\; m=\sum_{i=1}^n \omega(\xi_i)\xi_i^2 \implies \nonumber \\
W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{y(x+\xi_i)-2y(x)+y(x-\xi_i)}{\xi_i}\right)^2
\end{align}
%

Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(y(x-\zeta)\) is ill-defined. 
For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
\subsection{Results}
The simplest test case for this model is a linear-elastic beam with a square profile.
The models below were constrained to purely vertical movement of each point in order to reduce the total number of degrees of freedom, speeding evaluation and improving convergence.
For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.
Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:eppt_g100}.

\begin{figure}[h]
  \centering
  \scalebox{.55}{\input{\plotpath/elastic_h20_g2000.pgf}}
  \caption{The uniform-load elastic beam is accurately modeled with few nodes}
  \label{fig:eppt_g100}
\end{figure}

As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
This behavior is mimicked by the plasticity of the longest bond-pairs, producing the results shown in \cref{fig:eppu_h10_g2000}.
To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
\begin{figure}[h]
  \centering
  \scalebox{.55}{\input{\plotpath/eppu_h10_g2000.pgf}}
  \caption{The elastic perfectly-plastic beam requires finer discretization}
  \label{fig:eppu_h10_g2000}
\end{figure}

A material that is plastically deformed does not return to its original state when unloaded.
For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticity}. 
Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.

\begin{figure}[h]
\minipage{0.45\textwidth}
  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000.pgf}}
\endminipage\hfill
\minipage{0.45\textwidth}%
  \scalebox{.45}{\input{\plotpath/unloaded_n1000_g2000.pgf}}
\endminipage
\caption{Residual plastic deformation in an unloaded beam}
\label{fig:ResidualPlasticity}
\end{figure}

It is more difficult to verify the brittle material model because brittle failure is unstable.
When a crack begins, moment is transferred to other bond pairs, and failure progresses creating a plastic hinge.
This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have not failed.

\begin{figure}[h]
  \centering
  \scalebox{.65}{\input{\plotpath/brittle_h10_n200.pgf}}
  \caption{A brittle beam with prescribed center displacement}
  \label{fig:brittleBeam}
\end{figure}

Unlike a local model, partial failure is observed at nodes near the plastic hinge, as pairs of bonds that straddle the hinge are broken.

\section{Conclusion}

As far as we know, this the first peridynamic state based thin feature model, and results in accurate deformation results for simple beam tests.
The proposed damage model successfully reproduces the impact of nonlinear elasticity on deformation of a rectangular cantilever, and the framework is laid to allow application of the same model to I-beams.
It simplifies treatment of bending in beams, and is extensible to bending in plates.

\bibliographystyle{plain}
\bibliography{jogrady_bibdesk}

\end{document} 
\end

### 2013-12-27 BeamPaper.tex
Rewrite energy equivalence section

@@
 \usepackage{cleveref}
-\usepackage{autonum}
+%\usepackage{autonum}
 
@@
 %
-We will begin with the assumptions from Euler beam theory: length much greater than thickness, small displacements, and small rotations. 
-The latter two assumptions allow us to simplify our equations. 
+To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Euler-Bernoulli beam in the \emph{local limit}, i.e.
+when the nonlocal length scale vanishes.
+We will begin with the assumptions from Euler beam theory: the length of the beam is much greater than thickness, vertical displacements are small, and rotations are small.
+For small vertical displacments we have
 %
 \begin{equation}
-\label{eq:beam}
-\theta(\vstate{Y}{}{\xi})\approx \sin(\theta(\vstate{Y}{}{\xi})) = \frac{(\vstate{Y}{}{\xi})_y}{|\vstate{Y}{}{\xi}|} \approx \frac{y(x+\xi)-y(x)}{\xi}
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi},
+\label{eq:beamdtheta}
 \end{equation}
 %
+where $y$ is the vertical displacement of material point.  Using a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta})  
+%
 \begin{equation}
-\label{eq:beamdtheta}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi y'' +\mathcal{O}(\xi^3) 
+\label{eq:beamdtheta2}
 \end{equation}
 %
-Using a second order Taylor series to approximate $y$ around $x$, this last term in \cref{eq:beamdtheta} becomes a function of the second derivative of displacement, which we will call \(\kappa\).
-%
-\begin{equation}
-\label{eq:beamdtheta2}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi \kappa+\mathcal{O}(\xi^3) 
-\end{equation}
-%
-and if the curvatures are also small enough,
+substituting eq.~(\ref{eq:beamtheta2}) into the equation for the strain energy density of a single bond-pair,
 %
@@
 \label{eq:continuousBeamw}
-w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \alpha\frac{\xi^2}{2}\kappa^2 +\mathcal{O}(\xi^4) .
+w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(y'')^2 +\mathcal{O}(\xi^4).
 \end{align}
 %
-If we use a weighting function \(\omega(\xi)=\omega(|\xi|)\), the resulting strain energy density for the continuous peridynamic beam is
+If we use a weighting function \(\omega(\xi)=\omega(|\xi|)\) and assume that the $\omega$ plays the role of a localization kernel, i.e.
+$\omega = 0 \, \forall \, \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic beam is
 %
 \begin{equation}
-W \approx \int_{-\delta}^\delta \omega(\xi)\alpha\left(\frac{\xi^2}{2}\kappa^2 +\mathcal{O}(\xi^4)\right) d\xi = \frac{\alpha}{2}\left(\kappa^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 d\xi +\int_{-\delta}^\delta \omega(\xi)\mathcal{O}(\xi^4)d\xi\right) .
+W = \frac{\alpha}{2}(y'')^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 {\rm d}\xi + \mathcal{O}(\delta^5).
 \end{equation}
 %
-By choosing \(\alpha\) corresponding to our choices of weighting function, peridynamic horizon, and beam geometric and material properties, we can ensure that the potential energy density associated with a well-behaved deformation matches the prediction of Euler beam theory.
+Equating $W$ with the classical Euler-Bernoulli beam strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
 %
 \begin{align}
-\label{eq:classicbeam}
-\alpha = \frac{c}{m} ;\; c= EI ;\; m=\int_{-\delta}^\delta \omega(\xi)\xi^2 d\xi \implies W=\frac{EI}{2}\kappa^2+\mathcal{O}(\delta^2)
+    \lim_{\delta \to 0}  W &= \Omega, \notag \\
+    \frac{\alpha}{2} m (y'')^2 &= \frac{EI}{2} (y'')^2, \notag \\
+    \alpha &= \frac{EI}{m},
+\label{eq:alpha}
 \end{align}
 %
+with 
+\begin{equation}
+    m = \int_{-\delta}^{\delta} \omega(\xi) \xi^2 {\rm d}\xi \notag.
+\end{equation}
 

### 2013-12-30 BeamPaper.tex
removed eqn numbers
fixed coefficient and cleaned up equations in Eringen nonlocality comparison

@@
 \label{eq:PDCoPV}
-\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x})
+\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
 \end{equation}
@@
 \label{eq:PDstateEoM}
-\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),
+\rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),\notag
 \end{equation}
@@
 %
-substituting eq.~(\ref{eq:beamtheta2}) into the equation for the strain energy density of a single bond-pair,
+substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
 %
@@
 \label{eq:continuousBeamw}
-w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(y'')^2 +\mathcal{O}(\xi^4).
+w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(y'')^2 +\mathcal{O}(\xi^4).\notag
 \end{align}
@@
 \begin{equation}
-W = \frac{\alpha}{2}(y'')^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 {\rm d}\xi + \mathcal{O}(\delta^5).
+W = \frac{\alpha}{2}(y'')^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 {\rm d}\xi + \mathcal{O}(\delta^5).\notag
 \end{equation}
@@
 \begin{align}
-M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy \\
+M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy\notag \\
 %
-M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi
+M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi\notag
 \end{align}
@@
 \begin{equation}
-\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}
+\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}\notag
 \end{equation}
@@
 \begin{align}
-  M_\text{classical} &= 2 \int_{0}^{y_e}E b(y)y^2 \kappa dy +2 \int_{y_e}^{\frac{t}{2}}E b(y) \epsilon_c y dy \\
-  M_\text{PD} &= 2 \int_{0}^{\delta_e}\alpha \omega(\xi) \xi^2 \kappa d\xi +2 \int_{\delta_e}^{\delta}\alpha \omega(\xi) \Delta\theta_c \xi d\xi 
+  M_\text{classical} &= 2 \int_{0}^{y_e}E b(y)y^2 \kappa dy +2 \int_{y_e}^{\frac{t}{2}}E b(y) \epsilon_c y dy\notag \\
+  M_\text{PD} &= 2 \int_{0}^{\delta_e}\alpha \omega(\xi) \xi^2 \kappa d\xi +2 \int_{\delta_e}^{\delta}\alpha \omega(\xi) \Delta\theta_c \xi d\xi \notag
 \end{align}
@@
 \begin{equation}
-\label{eq:beamdtheta2}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)=  \pi-\xi \kappa-\frac{\xi^3}{12} \kappa''+\mathcal{O}(\xi^5)
+\label{eq:beamdthetaHOT}
+%\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)=  \pi-\xi \kappa-\frac{\xi^3}{12} \kappa''+\mathcal{O}(\xi^5)\notag
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \arctan\left(\pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)\right)\notag
 \end{equation}
 %
-and for the strain energy
+and for the strain energy (substituting \(\kappa = y''\) for readability),
 %
@@
 \begin{equation}
-W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{\xi^4}{24}\kappa^4+\mathcal{O}(\xi^6)) d\xi .
+%W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{\xi^4}{24}\kappa^4+\mathcal{O}(\xi^6)) d\xi .\notag
+W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{3\; \xi^4}{8}\kappa^4+\mathcal{O}(\xi^6)) d\xi .\notag
 \end{equation}
@@
 As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
-We can picture a nonlocal modulus based on the nonlocal curvature \(\bar{\kappa}= (\kappa + \frac{\xi^2}{12}\kappa'')\), so that 
+We can picture a nonlocal modulus based on the nonlocal curvature \(\bar{\kappa}= (\kappa + \frac{\xi^2}{6}\kappa'')\), so that 
 %
 \begin{equation}
-W \approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .
+W \approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
 \end{equation}
@@
 \begin{align}
-\label{eq:discreteBeamw}
-w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}\right)^2
+%\label{eq:discreteBeamw}
+w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}\right)^2 \notag
 \end{align}
@@
 \alpha &= \frac{c\; \Delta x}{m} ;\; c= EI ;\; m=\sum_{i=1}^n \omega(\xi_i)\xi_i^2 \implies \nonumber \\
-W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{y(x+\xi_i)-2y(x)+y(x-\xi_i)}{\xi_i}\right)^2
+W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{y(x+\xi_i)-2y(x)+y(x-\xi_i)}{\xi_i}\right)^2\notag
 \end{align}

### 2014-01-07 BeamPaper.tex
changed an out of place zeta to xi in discretization

@@
 
-Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(y(x-\zeta)\) is ill-defined. 
+Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(y(x-\xi_i)\) is ill-defined. 
 For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 

### 2014-01-30 BeamPaper.tex
add subsection on gradient local beams

@@
 Because many analyses of interest are partly or wholly comprised of these types of features, their development is an important addition to the capabilities of peridynamic analysis.
+%
+%The second section of this paper provides a brief introduction to peridynamics, including state based models.
+%The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
+%The fourth section demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
+%The fifth section demonstrates the beam model with simple test cases.
+The remainder of this introduction reviews other nonlocal work and provides a brief introduction to peridynamics, including state based models.
+\Cref{sec:ModelDev} presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
+\Cref{sec:EringenCompare} demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
+\Cref{sec:Numerical} demonstrates the beam model with simple test cases.
+%
+\subsection{Nonlocal Beam Models}
+\label{sec:NLbeams}
+%
+Nonlocal elasticity generally allows for forces at a point that are dependent on the material configuration of an entire body, rather than the configuration at that point.\cite{eringen1972nonlocal}
+While long-range forces are obvious at the molecular model, material at larger scales is conventionally modeled as though internal forces are local or contact forces.\cite{kroner1967elasticity}
+The result of such approximation is accurate for deformations that are homogenous, but introduces some inaccuracy for inhomogenous deformations like the propagation of waves with short wavelengths.
+One way to distinguish between homogenous and inhomogenous deformations is to incorporate higher-order gradients of deformation.
+While stress in classical elasticity is a function of the (first) gradient of deformation, Eringen's formulation of a nonlocal modulus in \cite{eringen1983differential} approximates a weighted sum of the first and second order gradients.
+This introduces a length scale to the model and has the effect of smearing out local deformation inhomogeneities over the surrounding material, while maintaining the conventional result for homogenous deformations.
 
-The second section of this paper provides a brief introduction to peridynamics, including state based models.
-The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
-The fourth section compares the model to Eringen's nonlocal elasticity for small peridynamic horizons.
-The fifth section demonstrates the beam model with simple test cases.
+Previous work in the nonlocal mechanics of beams is motivated by the observed stiffening of nanoscale cantilevers.
+Challamel and Wang demonstrate in \cite{Challamel2008small} that Eringen nonlocal elasticity cannot reproduce the scale stiffening, but that stiffening does result from other gradient-elastic models and models incorporating nonlocal curvature.
+Because all of these models incorporate higher-order gradients of deformation, they impose stronger continuity requirements than classical elasticity, and are unsuitable for discontinuous displacements.
+Because the gradients are evaluated locally, gradient models are called \textit{weakly nonlocal}.
+
 %
-\section{Peridynamics}
+\subsection{Peridynamics}
 \label{sec:PDintro}
 The term \textit{peridynamic} was coined by Silling in \cite{silling2000reformulation} and alludes to the fact that the force at a point is affected by nearby material configuration.
-Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
-These higher-order derivatives impose greater stronger continuity requirements than the classical model. 
-By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation 
+In contrast to gradient models, the peridynamic model is \textit{strongly nonlocal} and casts material behavior at a point as the \textit{integral} equation 
 %
@@
 \FloatBarrier
+%
 \section{Model Development}
+\label{sec:ModelDev}
 Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
@@
 \subsection{Energy Equivalence}
+\label{sec:EnergyEq}
 %
@@
 \subsection{Weighting Function and Perfect Plasticity}
+\label{sec:WeightFunction}
 The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
@@
 \section{Relation to Eringen Nonlocality}
+\label{sec:EringenCompare}
 %If we relax our homogeneity assumption somewhat, we recover from \cref{eq:beamdtheta} slightly more complex expressions for change in angle
@@
 \section{Numerical Simulation}
+\label{sec:Numerical}
 \subsection{Discretized Model}
+\label{sec:Discretized}
 For analysis purposes, it is often useful to represent a continuum part with a discrete version. 
@@
 \subsection{Results}
+\label{sec:Results}
 The simplest test case for this model is a linear-elastic beam with a square profile.
@@
 \section{Conclusion}
+\label{sec:Conclusion}
 

### 2014-02-03 BeamPaper.tex
filled out Numerical Simulation section with discrete EoM

@@
 %\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)=  \pi-\xi \kappa-\frac{\xi^3}{12} \kappa''+\mathcal{O}(\xi^5)\notag
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \arctan\left(\pi-\xi \frac{\partial^2 y}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 y}{\partial x^4}  +\mathcal{O}(\xi^5)\right)\notag
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \arctan\left(\pi-\xi \frac{\partial^2 v}{\partial x^2} -\frac{\xi^3}{12} \frac{\partial^4 v}{\partial x^4}  +\mathcal{O}(\xi^5)\right)\notag
 \end{equation}
 %
-and for the strain energy (substituting \(\kappa = y''\) for readability),
+and for the strain energy (substituting \(\kappa = v''\) for readability),
 %
@@
 %\label{eq:discreteBeamw}
-w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi}\right)^2 \notag
+w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{v(x+\xi)-2v(x)+v(x-\xi)}{\xi}\right)^2 \notag
 \end{align}
@@
 \alpha &= \frac{c\; \Delta x}{m} ;\; c= EI ;\; m=\sum_{i=1}^n \omega(\xi_i)\xi_i^2 \implies \nonumber \\
-W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{y(x+\xi_i)-2y(x)+y(x-\xi_i)}{\xi_i}\right)^2\notag
+W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{v(x+\xi_i)-2v(x)+v(x-\xi_i)}{\xi_i}\right)^2\notag
 \end{align}
 %
+Discretization of the original model results in the equation of motion
+\begin{equation}
+\rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})+\sum_i \omega(\xi_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times\left[\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right]-\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |}\right]\right\}\notag
+\end{equation}
+with
+\begin{align}
+\mathbf{p}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
+\mathbf{q}_i &= -\boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}-\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
+\mathbf{r}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+2\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i).\notag
+\end{align}
+and for small displacements and rotations in a uniform beam,
+\begin{equation}
+\rho(x)\ddot{v}(x) = f(x)+\alpha \sum_i 2\omega(\xi_i)\frac{v(x-2\xi_i)-4v(x-\xi_i)+6v(x)-4v(x+\xi_i)+v(x+2\xi_i)}{\xi_i^2}\notag
+\end{equation}
+Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(x-\xi_i)\) is ill-defined. 
+For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
+%
+\subsection{Numerical Method}
+\label{sec:NumMethod}
+Model behavior was evaluated by implementing the discretized equation of motion.
+The case of a beam simply supported at both ends was chosen for simplicity in both evaluation and comparison.
+Boundary conditions such as clamped supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
 
-Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(y(x-\xi_i)\) is ill-defined. 
-For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
+Deformations for quasistatic loading were computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
+%
 \subsection{Results}

### 2014-02-04 BeamPaper.tex
corrected Eringen equivalence

@@
 \begin{equation}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\frac{y(x+\xi)-2y(x)+y(x-\xi)}{\xi},
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\frac{v(x+\xi)-2v(x)+v(x-\xi)}{\xi},
 \label{eq:beamdtheta}
@@
 %
-where $y$ is the vertical displacement of material point.  Using a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta})  
+where $v$ is the vertical displacement of material point.  Using a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta})  
 %
 \begin{equation}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 y}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi y'' +\mathcal{O}(\xi^3) 
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 v}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi \kappa +\mathcal{O}(\xi^3); 
 \label{eq:beamdtheta2}
 \end{equation}
+with
+\begin{equation}
+\kappa = \frac{\partial^2 v}{\partial x^2}.\notag
+\end{equation}
 %
-substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
+Substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
 %
@@
 \label{eq:continuousBeamw}
-w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(y'')^2 +\mathcal{O}(\xi^4).\notag
+w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(\kappa)^2 +\mathcal{O}(\xi^4).\notag
 \end{align}
@@
 \begin{equation}
-W = \frac{\alpha}{2}(y'')^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 {\rm d}\xi + \mathcal{O}(\delta^5).\notag
+W = \frac{\alpha}{2}\kappa^2 \int_{-\delta}^\delta \omega(\xi)\xi^2 {\rm d}\xi + \mathcal{O}(\delta^5).\notag
 \end{equation}
@@
     \lim_{\delta \to 0}  W &= \Omega, \notag \\
-    \frac{\alpha}{2} m (y'')^2 &= \frac{EI}{2} (y'')^2, \notag \\
+    \frac{\alpha}{2} m \kappa^2 &= \frac{EI}{2} \kappa^2, \notag \\
     \alpha &= \frac{EI}{m},
@@
 %
-and for the strain energy (substituting \(\kappa = v''\) for readability),
+and for the strain energy (again substituting \(\kappa = v''\) for readability),
 %
@@
 As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
-We can picture a nonlocal modulus based on the nonlocal curvature \(\bar{\kappa}= (\kappa + \frac{\xi^2}{6}\kappa'')\), so that 
+We can picture a bending resistance based on the nonlocal curvature  \(\bar{\kappa}\), so that 
 %
+\begin{align}
+\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\
+W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
+\end{align}
+%  
+The same analysis can be taken further to obtain higher-order energy terms with even powers of \(\xi\) and even order derivatives of \(\kappa\). 
+Not all of these higher-order terms can be separated into the product of a local curvature and nonlocal bending resistance.
+
+Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material.
 \begin{equation}
-W \approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
+\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}')\notag
 \end{equation}
-%  
-This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
-The same analysis can be taken further to obtain higher-order energy terms with even powers of \(\xi\) and even order derivatives of \(\kappa\). 
-Not all of these higher-order terms can be separated into the product of a local curvature and nonlocal modulus.
+In the local limit these relationships take the form of higher-order gradients.
+Using a modified bessel function (second kind) nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
+\begin{align}
+\left(1-\tau^2l^2\nabla^2\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
+\end{align}
+in which \(\tau^2l^2\) is a scale-based material parameter.
+For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\tau^2l^2\) we can see that this relationship could be reformulated as
+\begin{equation}
+\mathbf{t}=\left(1+\tau^2l^2\nabla^2\right)\boldsymbol{\sigma}.\notag
+\end{equation}
+
+%This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
+The similarity is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
 

### 2014-02-05 BeamPaper.tex
clarified eringen equivalence and changed more y displacements to v

@@
 
-Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material.
+Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus (denoted here as \(K(|\mathbf{x}'-\mathbf{x}|,\tau)\)) that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material through the integral
 \begin{equation}
-\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}')\notag
+\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
 \end{equation}
 In the local limit these relationships take the form of higher-order gradients.
-Using a modified bessel function (second kind) nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
+Using a decaying exponential nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
 \begin{align}
-\left(1-\tau^2l^2\nabla^2\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
+\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
 \end{align}
 in which \(\tau^2l^2\) is a scale-based material parameter.
-For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\tau^2l^2\) we can see that this relationship could be reformulated as
+For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
 \begin{equation}
-\mathbf{t}=\left(1+\tau^2l^2\nabla^2\right)\boldsymbol{\sigma}.\notag
+\mathbf{t}=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\boldsymbol{\sigma}.\notag
 \end{equation}

### 2014-02-05 BeamPaper.tex
more edits to Eringen section

@@
 As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
-We can picture a bending resistance based on the nonlocal curvature  \(\bar{\kappa}\), so that 
+We can picture a bending resistance based on the bond length and the nonlocal curvature  \(\bar{\kappa}\), so that 
 %
 \begin{align}
-\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\
+\label{eq:NLbending}
+ \omega(\xi)\alpha\bar{\kappa}&=  \omega(\xi)\alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
 W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
@@
 In the local limit these relationships take the form of higher-order gradients.
-Using a decaying exponential nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
+Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t\) and \(\sigma\) 
 \begin{align}
-\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
+\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)t&=\sigma,\notag
 \end{align}
 in which \(\tau^2l^2\) is a scale-based material parameter.
-For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
+For well-behaved \(t\) and \(\sigma\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
 \begin{equation}
-\mathbf{t}=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\boldsymbol{\sigma}.\notag
+\label{eq:NLstress}
+t=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\sigma.\notag
 \end{equation}
+If we consider the results of the previous section and let \(dM = y\sigma dA\) and \(\sigma = Ey\kappa\), the contribution to moment resulting from Eringen's nonlocal elasticity in a fiber at \(y\)
+\begin{equation}
+\label{eq:EringenMoment}
+E y^2 (\kappa+\tau^2l^2\kappa''), \\
+\end{equation}
+and the resulting strain energy
+\begin{equation}
+\label{eq:EringenEnergy}
+\int_{-\frac{t}{2}}^{\frac{t}{2}} b(y) E \frac{y^2}{2} \kappa (\kappa+\tau^2l^2\kappa'')  dy,\notag
+\end{equation}
+bear a striking resemblance to \cref{eq:NLbending}.
 
 %This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
-The similarity is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
+The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
 

### 2014-02-05 BeamPaper.tex
plots partially updated

@@
 \begin{figure}[h]
-\subinputfrom{\diagrampath}{WeightProfile.eps_tex}
-\caption{A cross-section dependent weight function}
-\label{fig:WeightProfile}
+\minipage[t]{0.5\textwidth}
+ \centering
+  \subinputfrom{\diagrampath}{WeightProfile_Uniform.eps_tex}
+\caption{Weight function for a beam of rectangular cross-section}
+\label{fig:WeightProfileUniform}
+\endminipage\hfill
+\minipage[t]{0.5\textwidth}%
+  \centering
+  \subinputfrom{\diagrampath}{WeightProfile_Ibeam.eps_tex}
+\caption{Weight function for an I-beam}
+\label{fig:WeightProfileIbeam}
+\endminipage
 \end{figure}
@@
 This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
-An example is shown in \cref{fig:WeightProfile}.
+Examples are shown in \cref{fig:WeightProfileUniform,fig:WeightProfileIbeam}.
 While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.
@@
 For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.
-Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:eppt_g100}.
+Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:elastic_g2000}.
 
@@
   \centering
-  \scalebox{.55}{\input{\plotpath/elastic_h20_g2000.pgf}}
+  \scalebox{.65}{\input{\plotpath/elastic_h20_g2000_edit.pgf}}
   \caption{The uniform-load elastic beam is accurately modeled with few nodes}
-  \label{fig:eppt_g100}
+  \label{fig:elastic_g2000}
 \end{figure}
@@
   \centering
-  \scalebox{.55}{\input{\plotpath/eppu_h10_g2000.pgf}}
+  \scalebox{.65}{\input{\plotpath/eppu_h10_g2000_edit.pgf}}
   \caption{The elastic perfectly-plastic beam requires finer discretization}
@@
 
+%
 \begin{figure}[h]
-\minipage{0.45\textwidth}
-  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000.pgf}}
+\minipage[t]{0.5\textwidth}
+ \centering
+  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+\caption{N-convergence}
+\label{fig:ResidualPlasticityN}
 \endminipage\hfill
-\minipage{0.45\textwidth}%
-  \scalebox{.45}{\input{\plotpath/unloaded_n1000_g2000.pgf}}
+\minipage[t]{0.5\textwidth}%
+  \centering
+  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+\caption{H-convergence}
+\label{fig:ResidualPlasticityH}
 \endminipage
-\caption{Residual plastic deformation in an unloaded beam}
-\label{fig:ResidualPlasticity}
 \end{figure}

### 2014-02-06 BeamPaper.tex
diagrams and brittle plots prettied up

@@
 \begin{figure}[h]
-\subinputfrom{\diagrampath}{BondPairBending.eps_tex}
+\subinputfrom{\diagrampath}{BondPairBending_edit.eps_tex}
 \caption{Bond-pair moment contribution}
@@
   \centering
-  \scalebox{.65}{\input{\plotpath/elastic_h20_g2000_edit.pgf}}
+  \scalebox{.6}{\input{\plotpath/elastic_h20_g2000.pgf}}
   \caption{The uniform-load elastic beam is accurately modeled with few nodes}
@@
   \centering
-  \scalebox{.65}{\input{\plotpath/eppu_h10_g2000_edit.pgf}}
+  \scalebox{.6}{\input{\plotpath/eppu_h10_g2000.pgf}}
   \caption{The elastic perfectly-plastic beam requires finer discretization}
@@
 For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
-This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticity}. 
+This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticityN,fig:ResidualPlasticityH}. 
 Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.
@@
 \begin{figure}[h]
-\minipage[t]{0.5\textwidth}
   \centering
-  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
-\caption{N-convergence}
+  \scalebox{.6}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+  \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
   \label{fig:ResidualPlasticityN}
-\endminipage\hfill
-\minipage[t]{0.5\textwidth}%
+\end{figure}
+%
+\begin{figure}[h]
   \centering
-  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
-\caption{H-convergence}
+  \scalebox{.6}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+  \caption{Accurately modeling residual plastic deformation also requires a small horizon}
   \label{fig:ResidualPlasticityH}
-\endminipage
 \end{figure}
+%
+%\begin{figure}[h]
+%\minipage[t]{0.5\textwidth}
+% \centering
+%  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+%\caption{N-convergence}
+%\label{fig:ResidualPlasticityN}
+%\endminipage\hfill
+%\minipage[t]{0.5\textwidth}%
+%  \centering
+%  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+%\caption{H-convergence}
+%\label{fig:ResidualPlasticityH}
+%\endminipage
+%\end{figure}
 
 It is more difficult to verify the brittle material model because brittle failure is unstable.
-When a crack begins, moment is transferred to other bond pairs, and failure progresses creating a plastic hinge.
+When a crack begins, moment is transferred to other bond pairs, and failure progresses until every pair of bonds surrounding a node are broken, creating a hinge at that node.
 This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have not failed.

### 2014-02-06 BeamPaper.tex
added a line to the end of Eringen section

@@
 \Cref{sec:ModelDev} presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
-\Cref{sec:EringenCompare} demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
+\Cref{sec:EringenCompare} demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons.
 \Cref{sec:Numerical} demonstrates the beam model with simple test cases.
@@
 The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
+It is therefore unsurprising that, like Eringen's nonlocal elasticity, the peridynamic bending model fails to predict the stiffening associated with nanoscale cantilevers.
+Instead, the advantage of peridynamic models is their natural handling of discontinuities.
 

### 2014-02-17 BeamPaper.tex
Small changes/edits

--- 2014-02-05 BeamPaper.tex
@@
 
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
+%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
 
-\graphicspath{ {../} }
-\graphicspath{ {./images/} }
+\graphicspath{{../}}
+\graphicspath{{./images/}}
 \newcommand{\diagrampath}{./diagrams/}
@@
 \section{Introduction}
-The final goal of many mechanical engineering analyses is the prediction and description of material failure.
-When processes such as fracture are modeled, the differential equations of classical mechanics are ill-defined at the resulting discontinuities.
-A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement, so that discontinuities evolve naturally and require no special treatment.
-Various peridynamic models capture the material behavior of 3-dimensional solid objects, but would be very expensive to implement for a thin plate or beam.
-Other peridynamic models capture tension and compression in 1D bars and 2D plates, but these models do not resist transverse displacement.
-A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.
+A goal of many mechanical engineering analyses is the prediction and description of material failure.
+When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
+A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities evolve naturally and require no special treatment.
+Various peridynamic material models capture the material behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would cause an inordinate amount of computational nodes along the length in a long, slender structural object.
+Other peridynamic models capture tension and compression in 1D bars and 2D plates, but these models do not resist transverse displacement {\color{red} [Ref]}.
+A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness, to create a model that can represent thin structures, but fails to properly {\color{red} XXX}.
 
-This paper begins to remedy that lack in the simplest case by presenting a peridynamic equivalent to an Euler-Bernoulli beam.
+This paper presents a peridynamic equivalent to an Euler-Bernoulli beam, along with a methodology for representing non-uniform cross-sections, plastic behavior, and failure.
 In addition to directly modeling a thin beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
@@
 %The second section of this paper provides a brief introduction to peridynamics, including state based models.
-%The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
+%The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of vanishing nonlocality.
 %The fourth section demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
 %The fifth section demonstrates the beam model with simple test cases.
-The remainder of this introduction reviews other nonlocal work and provides a brief introduction to peridynamics, including state based models.
-\Cref{sec:ModelDev} presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
-\Cref{sec:EringenCompare} demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
-\Cref{sec:Numerical} demonstrates the beam model with simple test cases.
+The remainder of this introduction reviews other nonlocal models and provides a brief introduction to peridynamics, including state-based models.
+\Cref{sec:ModelDev} presents the state-based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
+\Cref{sec:EringenCompare} demonstrates the model's relationship to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
+\Cref{sec:Numerical} numerically demonstrates the beam model with simple test cases.
 %
@@
 %
-Nonlocal elasticity generally allows for forces at a point that are dependent on the material configuration of an entire body, rather than the configuration at that point.\cite{eringen1972nonlocal}
-While long-range forces are obvious at the molecular model, material at larger scales is conventionally modeled as though internal forces are local or contact forces.\cite{kroner1967elasticity}
+Nonlocal elasticity generally allows for forces at a point that are dependent on the material configuration of an entire body, rather than the configuration at that point \cite{eringen1972nonlocal}.
+While long-range forces are obvious at the molecular model, material at larger scales is conventionally modeled as though internal forces are local or contact forces \cite{kroner1967elasticity}.
 The result of such approximation is accurate for deformations that are homogenous, but introduces some inaccuracy for inhomogenous deformations like the propagation of waves with short wavelengths.
@@
 
-Introduced by Silling et al. in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
+Introduced by Silling et al.\ in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
 The most common states are scalar states and vector states which are scalar and vector valued, respectively.
@@
 Models in which they are not in the same direction are called \textit{non-ordinary}.
-Silling et al. demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
-Foster et al.
-\cite{foster2010viscoplasticity} and Warren et.
-al.
-\cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
+Silling et al.\ demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
+Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
 %
@@
 %
-To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Euler-Bernoulli beam in the \emph{local limit}, i.e.
-when the nonlocal length scale vanishes.
+To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Euler-Bernoulli beam in the \emph{local limit}, i.e.\ when the nonlocal length scale vanishes.
 We will begin with the assumptions from Euler beam theory: the length of the beam is much greater than thickness, vertical displacements are small, and rotations are small.
@@
 The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
-Consider an Euler beam in bending with curvature \(\kappa\). 
+Consider a classical Euler-Bernoulli beam in bending with curvature \(\kappa\). 
 Fibers running parallel to the neutral axis of the beam are stretched in proportion to their distance from the neutral axis, with strain \(\epsilon = y\kappa\). 
@@
 \begin{figure}[h]
-\minipage[t]{0.5\textwidth}
- \centering
-  \subinputfrom{\diagrampath}{WeightProfile_Uniform.eps_tex}
-\caption{Weight function for a beam of rectangular cross-section}
-\label{fig:WeightProfileUniform}
-\endminipage\hfill
-\minipage[t]{0.5\textwidth}%
-  \centering
-  \subinputfrom{\diagrampath}{WeightProfile_Ibeam.eps_tex}
-\caption{Weight function for an I-beam}
-\label{fig:WeightProfileIbeam}
-\endminipage
+\subinputfrom{\diagrampath}{WeightProfile.eps_tex}
+\caption{A cross-section dependent weight function}
+\label{fig:WeightProfile}
 \end{figure}
@@
 This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
-Examples are shown in \cref{fig:WeightProfileUniform,fig:WeightProfileIbeam}.
+An example is shown in \cref{fig:WeightProfile}.
 While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.
@@
 %W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{\xi^4}{24}\kappa^4+\mathcal{O}(\xi^6)) d\xi .\notag
-W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{3\; \xi^4}{8}\kappa^4+\mathcal{O}(\xi^6)) d\xi .\notag
+W \approx \int_{-\delta}^\delta \omega(\xi)\alpha(\frac{\xi^2}{2}\kappa^2+\frac{\xi^4}{12}\kappa\kappa''-\frac{3\; \xi^4}{8}\kappa^4+\mathcal{O}(\xi^6)) d\xi.\notag
 \end{equation}
@@
 As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
-We can picture a bending resistance based on the bond length and the nonlocal curvature  \(\bar{\kappa}\), so that 
+We can picture a bending resistance based on the nonlocal curvature  \(\bar{\kappa}\), so that 
 %
 \begin{align}
-\label{eq:NLbending}
- \omega(\xi)\alpha\bar{\kappa}&=  \omega(\xi)\alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
-W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
+\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\
+W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi.\notag
 \end{align}
@@
 
-Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus (denoted here as \(K(|\mathbf{x}'-\mathbf{x}|,\tau)\)) that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material through the integral
+Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material.
 \begin{equation}
-\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
+\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}')\notag
 \end{equation}
 In the local limit these relationships take the form of higher-order gradients.
-Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t\) and \(\sigma\) 
+Using a modified bessel function (second kind) nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
 \begin{align}
-\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)t&=\sigma,\notag
+\left(1-\tau^2l^2\nabla^2\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
 \end{align}
 in which \(\tau^2l^2\) is a scale-based material parameter.
-For well-behaved \(t\) and \(\sigma\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
+For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\tau^2l^2\) we can see that this relationship could be reformulated as
 \begin{equation}
-\label{eq:NLstress}
-t=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\sigma.\notag
+\mathbf{t}=\left(1+\tau^2l^2\nabla^2\right)\boldsymbol{\sigma}.\notag
 \end{equation}
-If we consider the results of the previous section and let \(dM = y\sigma dA\) and \(\sigma = Ey\kappa\), the contribution to moment resulting from Eringen's nonlocal elasticity in a fiber at \(y\)
-\begin{equation}
-\label{eq:EringenMoment}
-E y^2 (\kappa+\tau^2l^2\kappa''), \\
-\end{equation}
-and the resulting strain energy
-\begin{equation}
-\label{eq:EringenEnergy}
-\int_{-\frac{t}{2}}^{\frac{t}{2}} b(y) E \frac{y^2}{2} \kappa (\kappa+\tau^2l^2\kappa'')  dy,\notag
-\end{equation}
-bear a striking resemblance to \cref{eq:NLbending}.
 
 %This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
-The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
+The similarity is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
 
@@
 For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.
-Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:elastic_g2000}.
+Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:eppt_g100}.
 
@@
   \centering
-  \scalebox{.65}{\input{\plotpath/elastic_h20_g2000_edit.pgf}}
+  \scalebox{.55}{\input{\plotpath/elastic_h20_g2000.pgf}}
   \caption{The uniform-load elastic beam is accurately modeled with few nodes}
-  \label{fig:elastic_g2000}
+  \label{fig:eppt_g100}
 \end{figure}
@@
   \centering
-  \scalebox{.65}{\input{\plotpath/eppu_h10_g2000_edit.pgf}}
+  \scalebox{.55}{\input{\plotpath/eppu_h10_g2000.pgf}}
   \caption{The elastic perfectly-plastic beam requires finer discretization}
@@
 
-%
 \begin{figure}[h]
-\minipage[t]{0.5\textwidth}
- \centering
-  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
-\caption{N-convergence}
-\label{fig:ResidualPlasticityN}
+\minipage{0.45\textwidth}
+  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000.pgf}}
 \endminipage\hfill
-\minipage[t]{0.5\textwidth}%
-  \centering
-  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
-\caption{H-convergence}
-\label{fig:ResidualPlasticityH}
+\minipage{0.45\textwidth}%
+  \scalebox{.45}{\input{\plotpath/unloaded_n1000_g2000.pgf}}
 \endminipage
+\caption{Residual plastic deformation in an unloaded beam}
+\label{fig:ResidualPlasticity}
 \end{figure}

### 2014-02-17 BeamPaper.tex

--- 2014-02-06 BeamPaper.tex
@@
 %The second section of this paper provides a brief introduction to peridynamics, including state based models.
-%The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
+%The third section presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of vanishing nonlocality.
 %The fourth section demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons, and compares other gradient models.
@@
 \begin{align}
-\label{eq:NLbending}
- \omega(\xi)\alpha\bar{\kappa}&=  \omega(\xi)\alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
-W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
+\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\
+W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi.\notag
 \end{align}

### 2014-02-17 BeamPaper.tex
actually add new diagram and plot files

@@
-\documentclass[11pt]{amsart}
+\documentclass[5p,twocolumn]{elsarticle}
 \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
@@
 
-\title{Peridynamic Beams: \\ A Non-ordinary, State Based Model}
-\author{James O'Grady \and John T. Foster}
-%\date{}                                           % Activate to display a given date or no date
+\journal{International Journal of Solids and Structures}
 
 \begin{document}
+
+\begin{frontmatter}
+
+\title{Peridynamic Beams: \\ A Non-ordinary, State Based Model}
+
+\author[utsa]{James O'Grady\corref{cor1}}
+\ead{jogrady@gmail.com}
+
+\author[utsa]{John Foster\corref{cor2}}
+\ead{john.foster@utsa.edu}
+
+\cortext[cor1]{Principal Corresponding author}
+\cortext[cor2]{Corresponding author}
+
+\address[utsa]{The University of Texas at San Antonio, One UTSA Circle, San Antonio, TX 78249}
+%\date{}                                           % Activate to display a given date or no date
 
@@
 
-\maketitle
+\begin{keyword}
+Peridynamics \sep non-ordinary models
+\end{keyword}
+
+\end{frontmatter}
+%\maketitle
 
@@
 \begin{figure}[h]
-\subinputfrom{\diagrampath}{simpleBondPair.eps_tex}
+\centering
+\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{simpleBondPair.eps_tex}}
 \caption{Illustration of a bond pair model that resists angular deformation}
@@
 \begin{figure}[h]
-\subinputfrom{\diagrampath}{bondPair.eps_tex}
+\centering
+\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{bondPair.eps_tex}}
 \caption{Deformation and force vector states}
@@
 %
-\begin{equation}
-\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) \approx \pi-\xi \frac{\partial^2 v}{\partial x^2}+\mathcal{O}(\xi^3) =  \pi-\xi \kappa +\mathcal{O}(\xi^3); 
+\begin{align}
+\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}) &\approx \pi-\xi \frac{\partial^2 v}{\partial x^2}+\mathcal{O}(\xi^3) \notag \\
+&\approx  \pi-\xi \kappa +\mathcal{O}(\xi^3); 
 \label{eq:beamdtheta2}
-\end{equation}
+\end{align}
 with
@@
 \label{eq:continuousBeamw}
-w = \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] = \omega(\xi) \alpha\frac{\xi^2}{2}(\kappa)^2 +\mathcal{O}(\xi^4).\notag
+w &= \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \notag\\
+&\approx \omega(\xi) \alpha\frac{\xi^2}{2}(\kappa)^2 +\mathcal{O}(\xi^4).\notag
 \end{align}
@@
 \begin{figure}[h]
-\subinputfrom{\diagrampath}{EulerBending.eps_tex}
+\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{EulerBending.eps_tex}}
 \caption{Euler beam moment contribution}
@@
 \begin{figure}[h]
+\centering
 \subinputfrom{\diagrampath}{BondPairBending_edit.eps_tex}
@@
 \begin{align}
-M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy\notag \\
+M_\text{E}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA &= \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy\notag \\
 %
-M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi\notag
+M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi &\notag \\
+&= \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: &\approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi\notag
 \end{align}
@@
 \begin{figure}[h]
-\minipage[t]{0.5\textwidth}
  \centering
@@
 \label{fig:WeightProfileUniform}
-\endminipage\hfill
-\minipage[t]{0.5\textwidth}%
+\end{figure}
+
+\begin{figure}
   \centering
@@
 \label{fig:WeightProfileIbeam}
-\endminipage
 \end{figure}
@@
 \begin{align}
-\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\
+\label{eq:NLbending}
+\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
 W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi.\notag
@@
 
-%This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
 The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
@@
 %\label{eq:discreteBeamw}
-w = \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \approx \frac{\alpha}{2}\left(\frac{v(x+\xi)-2v(x)+v(x-\xi)}{\xi}\right)^2 \notag
+w &= \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \notag \\
+&\approx \frac{\alpha}{2}\left(\frac{v(x+\xi)-2v(x)+v(x-\xi)}{\xi}\right)^2 \notag
 \end{align}
@@
 Discretization of the original model results in the equation of motion
-\begin{equation}
-\rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})+\sum_i \omega(\xi_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times\left[\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right]-\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |}\right]\right\}\notag
-\end{equation}
+\begin{align}
+\rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})&+\sum_i \omega(\xi_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \left[ \frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right] \right.
+\notag \\
+& \left.
+-\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |} \right] \right\} \notag
+\end{align}
 with
@@
 and for small displacements and rotations in a uniform beam,
-\begin{equation}
-\rho(x)\ddot{v}(x) = f(x)+\alpha \sum_i 2\omega(\xi_i)\frac{v(x-2\xi_i)-4v(x-\xi_i)+6v(x)-4v(x+\xi_i)+v(x+2\xi_i)}{\xi_i^2}\notag
-\end{equation}
+\begin{align}
+&\rho(x)\ddot{v}(x) = f(x)+\alpha \sum_i 2\omega(\xi_i)\bigg( \notag\\
+&\left. \frac{v(x-2\xi_i)-4v(x-\xi_i)+6v(x)-4v(x+\xi_i)+v(x+2\xi_i)}{\xi_i^2}\right) \notag
+\end{align}
 Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(x-\xi_i)\) is ill-defined. 
@@
   \centering
-  \scalebox{.6}{\input{\plotpath/elastic_h20_g2000.pgf}}
+  \resizebox{\linewidth}{!}{\input{\plotpath/elastic_h20_g2000.pgf}}
   \caption{The uniform-load elastic beam is accurately modeled with few nodes}
@@
   \centering
-  \scalebox{.6}{\input{\plotpath/eppu_h10_g2000.pgf}}
+  \resizebox{\linewidth}{!}{\input{\plotpath/eppu_h10_g2000.pgf}}
   \caption{The elastic perfectly-plastic beam requires finer discretization}
@@
   \centering
-  \scalebox{.6}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+  \resizebox{\linewidth}{!}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
   \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
@@
   \centering
-  \scalebox{.6}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+  \resizebox{\linewidth}{!}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
   \caption{Accurately modeling residual plastic deformation also requires a small horizon}
@@
 \end{figure}
-%
-%\begin{figure}[h]
-%\minipage[t]{0.5\textwidth}
-% \centering
-%  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
-%\caption{N-convergence}
-%\label{fig:ResidualPlasticityN}
-%\endminipage\hfill
-%\minipage[t]{0.5\textwidth}%
-%  \centering
-%  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
-%\caption{H-convergence}
-%\label{fig:ResidualPlasticityH}
-%\endminipage
-%\end{figure}
 
@@
   \centering
-  \scalebox{.65}{\input{\plotpath/brittle_h10_n200.pgf}}
+  \resizebox{\linewidth}{!}{\input{\plotpath/brittle_h10_n200.pgf}}
   \caption{A brittle beam with prescribed center displacement}

### 2014-02-17 BeamPaper.tex
that last push was actually changing format to work with twocolumn elsarticle
added references and fleshed out Taylor model in intro

@@
 \address[utsa]{The University of Texas at San Antonio, One UTSA Circle, San Antonio, TX 78249}
-%\date{}                                           % Activate to display a given date or no date
 
@@
 \end{frontmatter}
-%\maketitle
 
@@
 Various peridynamic material models capture the material behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would cause an inordinate amount of computational nodes along the length in a long, slender structural object.
-Other peridynamic models capture tension and compression in 1D bars and 2D plates, but these models do not resist transverse displacement {\color{red} [Ref]}.
-A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness, to create a model that can represent thin structures, but fails to properly {\color{red} XXX}.
+Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.
+A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness. 
+This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading. 
+The model is limited to the 3D bond-based poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
 
 This paper presents a peridynamic equivalent to an Euler-Bernoulli beam, along with a methodology for representing non-uniform cross-sections, plastic behavior, and failure.  
+This model is not derived from prior ordinary peridynamic models based on bond extension, but directly resists bending deformation.
 In addition to directly modeling a thin beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{elsarticle-num}
 \bibliography{jogrady_bibdesk}

### 2014-02-20 BeamPaper.tex
Small changes

@@
 
-\title{Peridynamic Beams: \\ A Non-ordinary, State Based Model}
+\title{Peridynamic beams: A non-ordinary, state-based model}
 
@@
 While multiple peridynamic material models capture the behavior of solid materials, this is the first 1D state based peridynamic model to resist bending.
-For sufficiently homogenous and differentiable displacements, the model is shown to be equivalent to Eringen's nonlocal elasticity.
+For sufficiently homogeneous and differentiable displacements, the model is shown to be equivalent to Eringen's nonlocal elasticity.
 As the peridynamic horizon approaches 0, it reduces to the classical Euler-Bernoulli beam equations.
@@
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  
-A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities evolve naturally and require no special treatment.
-Various peridynamic material models capture the material behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would cause an inordinate amount of computational nodes along the length in a long, slender structural object.
+A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.
+Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.
 Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.
@@
 This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading. 
-The model is limited to the 3D bond-based poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
+The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
 
@@
 This model is not derived from prior ordinary peridynamic models based on bond extension, but directly resists bending deformation.
-In addition to directly modeling a thin beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
+In addition to directly modeling a beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
 Because many analyses of interest are partly or wholly comprised of these types of features, their development is an important addition to the capabilities of peridynamic analysis.
@@
 \Cref{sec:ModelDev} presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
-\Cref{sec:EringenCompare} demonstrates the model's equivalence to Eringen's nonlocal elasticity for small peridynamic horizons.
-\Cref{sec:Numerical} demonstrates the beam model with simple test cases.
+\Cref{sec:EringenCompare} demonstrates the model's relationship to Eringen's nonlocal elasticity for small peridynamic horizons.
+\Cref{sec:Numerical} demonstrates the beam model with simple numerical examples.
 %
@@
 While long-range forces are obvious at the molecular model, material at larger scales is conventionally modeled as though internal forces are local or contact forces \cite{kroner1967elasticity}.
-The result of such approximation is accurate for deformations that are homogenous, but introduces some inaccuracy for inhomogenous deformations like the propagation of waves with short wavelengths.
-One way to distinguish between homogenous and inhomogenous deformations is to incorporate higher-order gradients of deformation.
+The result of such approximation is accurate for deformations that are homogeneous, but introduces some inaccuracy for inhomogeneous deformations like the propagation of waves with short wavelengths.
+One way to distinguish between homogeneous and inhomogeneous deformations is to incorporate higher-order gradients of deformation.
 While stress in classical elasticity is a function of the (first) gradient of deformation, Eringen's formulation of a nonlocal modulus in \cite{eringen1983differential} approximates a weighted sum of the first and second order gradients.
-This introduces a length scale to the model and has the effect of smearing out local deformation inhomogeneities over the surrounding material, while maintaining the conventional result for homogenous deformations.
+This introduces a length scale to the model and has the effect of smearing out local deformation inhomogeneities over the surrounding material, while maintaining the conventional result for homogeneous deformations.
 
@@
 The term \textit{peridynamic} was coined by Silling in \cite{silling2000reformulation} and alludes to the fact that the force at a point is affected by nearby material configuration.
-In contrast to gradient models, the peridynamic model is \textit{strongly nonlocal} and casts material behavior at a point as the \textit{integral} equation 
+In contrast to gradient models, the peridynamic model is \textit{strongly nonlocal} and casts material behavior at a point as the \textit{integral equation} 
 %
@@
 %
-rather than the classical \textit{differential} equation.
-Instead of the divergence of stress, we have the integral of a ``force" function $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$.
-This force function may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.
+rather than the classical \textit{partial-differential equation}.
+Instead of the divergence of stress, we have the integral of a ``force" functional $\mathbi{f}$ of the position vectors $\mathbf{x}$ and  $\mathbf{q}$ of a point within the body domain $\Omega$. 
+This force functional may depend on $\mathbf{x}$, $\mathbf{q}$, their deformed positions, the original and deformed positions of other points in $\Omega$, history, etc.
 
 Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
-While the simplest force functions recreate a one-parameter linear elastic solid material\cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors\cite{silling2005peridynamic}.
-To describe force functions that incorporate the behavior of all points in the nearby material (not just \(\mathbf{x}\) and \(\mathbf{q}\)), we must introduce the concept of a peridynamic state.
+While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic}.
+
+To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic state.
 
 Introduced by Silling et al.\ in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
-The most common states are scalar states and vector states which are scalar and vector valued, respectively.
-Unlike multiplication by a second order tensor, which can only map vectors linearly to other vectors, vector states can produce highly nonlinear or even discontinuous mappings.
-Important properties of states are magnitude and direction, while important operations include the addition and decomposition of states, inner and tensor products, and the Fr\'{e}chet derivative of a function with respect to a state~\cite{silling2007peridynamic}.
+The most common states are scalar-states and vector-states which are scalar and vector valued, respectively.
+Unlike a second order tensor, which can only map vectors linearly to other vectors, vector-states can produce nonlinear or even discontinuous mappings.
+Important properties of states are magnitude and direction, while important operations include the addition and decomposition of states, inner and tensor products, and the Fr\'{e}chet derivative of a function with respect to a state \cite{silling2007peridynamic}.
 
-Conservation of linear momentum in the \textit{state based} peridynamic formulation results in the equation of motion,
+Conservation of linear momentum in the \textit{state-based} peridynamic formulation results in the equation of motion,
 %
@@
 in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
-The deformed image of the vector $\mathbf{q}-\mathbf{x}$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation}. 
+The deformed image of the vector $\mathbf{q-x}$) is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation}. 
 %
@@
 Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.
-If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.
-Models in which they are not in the same direction are called \textit{non-ordinary}.
+If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' (i.e.\ the vector $\mathbf{q-x}$ between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.
+Models in which the bond-force interactions are not in the same direction as the deformed bond are called \textit{non-ordinary}.
 Silling et al.\ demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
-Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
+Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} show that some correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state-based constitutive models for finite deformations.
 %
@@
 %
-\section{Model Development}
+\section{A non-ordinary beam model}
 \label{sec:ModelDev}
-Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
+Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond-vector originating from a point is connected by a rotational spring to its opposite originating from that same point.
 %
@@
 Because the potential energy and force states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}. 
-Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.
+Other choices for the bond-pair potential function, such as $w = (\pi - \theta)^2$, are also possible, but result in more mathematically complex analysis.
+
 \subsection{Energy Equivalence}
@@
 We will begin with the assumptions from Euler beam theory: the length of the beam is much greater than thickness, vertical displacements are small, and rotations are small.
-For small vertical displacments we have
+For small vertical displacements (i.e.\ $\sin{\theta} \approx \theta$) we have
 %
@@
 %
-where $v$ is the vertical displacement of material point.  Using a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta})  
+where $v$ is the vertical displacement of material point.  Momentarily assuming that $v$ is continuous and using a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta})  
 %
@@
 If we use a weighting function \(\omega(\xi)=\omega(|\xi|)\) and assume that the $\omega$ plays the role of a localization kernel, i.e.
-$\omega = 0 \, \forall \, \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic beam is
+$\omega = 0 \,\, \forall \,\, \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic beam is
 %
@@
 
-\subsection{Weighting Function and Perfect Plasticity}
+\subsection{Weighting function and perfect plasticity}
 \label{sec:WeightFunction}
@@
 \begin{equation}
-\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}\notag
+\omega(\xi) = |\xi| b\left(y\right) \quad \text{at} \quad y=\frac{\xi}{\delta} \frac{t}{2}\notag
 \end{equation}
@@
 
-In a bent Elastic Perfectly Plastic beam, axial fibers are still stretched in proportion to their distance from the neutral axis, but the relationship \(\sigma = E\epsilon = Ey\kappa\) only holds for \(|\epsilon| = |y\kappa| < \epsilon_c\).
+In a deformed elastic perfectly-plastic beam, axial fibers are still stretched in proportion to their distance from the neutral axis, but the relationship \(\sigma = E\epsilon = Ey\kappa\) only holds for \(|\epsilon| = |y\kappa| < \epsilon_c\).
 For greater stretches, the relationship becomes \(\sigma = \pm E\epsilon_c \). 

### 2014-02-20 BeamPaper.tex
minor changes re 20Feb meeting

@@
 \usepackage{amssymb}
+\usepackage{mathtools}
 \usepackage{epstopdf}
@@
 \begin{equation}
-\omega(\xi) = |\xi| b\left(y\right) \quad \text{at} \quad y=\frac{\xi}{\delta} \frac{t}{2}\notag
+\label{eq:WeightFunction}
+\omega(\xi) = |\xi| b\left(y\right) \quad \text{at} \quad y=\frac{\xi}{\delta} \frac{t}{2}
 \end{equation}
@@
 This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
-Examples are shown in \cref{fig:WeightProfileUniform,fig:WeightProfileIbeam}.
+An example for a rectangular beam is illustrated in \cref{fig:WeightProfileUniform}.
+For an I beam with height \(h_\text{beam}\), width \(w_\text{beam}\), web height \(h_\text{web}\), and web width \(w_\text{web}\), substituting the beam profile
+\begin{equation}
+b(y) = 
+  \begin{dcases}
+    w_\text{web} & \text{if } |y| \leq \frac{h_\text{web}}{2} \\
+    w_\text{beam} & \text{if } \frac{h_\text{web}}{2} < |y| \leq \frac{h_\text{beam}}{2} \\
+    0 &\text{otherwise}
+  \end{dcases}\notag
+\end{equation}
+into \cref{eq:WeightFunction} gives the weight function
+\begin{equation}
+\omega(\xi) = 
+  \begin{dcases}
+    w_\text{web} & \text{if } |\xi| \leq \delta\frac{h_\text{web}}{h_\text{beam}} \\
+    w_\text{beam} & \text{if } \delta\frac{h_\text{web}}{h_\text{beam}} < |\xi| \leq \delta \\
+    0 &\text{otherwise}
+  \end{dcases}\notag
+\end{equation}
+and is ilustrated in \cref{fig:WeightProfileIbeam}.
     While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.
@@
 As the horizon \(\delta\) becomes small, higher-order \(\xi\) terms become relatively less important, and \(\xi^4\kappa^4\) is dominated by \(\xi^2\kappa^2\) for large \(\kappa\) and by \(\xi^4\kappa\kappa''\) for small \(\kappa\).
-We can picture a bending resistance based on the bond length and the nonlocal curvature  \(\bar{\kappa}\), so that 
+The remaining terms can be rearranged,
+\begin{align}
+W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa(\kappa + \frac{\xi^2}{6}\kappa'') d\xi, \notag
+\end{align}
+in a manner strongly suggesting an alternative bending resistance term.
+We can picture a bending resistance based on the bond length and proportional to the nonlocal curvature  \(\bar{\kappa}=(\kappa + \frac{\xi^2}{6}\kappa'')\), so that 
 %
@@
 \label{eq:NLbending}
-\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
-W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi.\notag
+\bar{\kappa}&=(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\
+W &\approx \int_{-\delta}^\delta \omega(\xi)\alpha \frac{\xi^2}{2}\kappa\bar{\kappa}d\xi .\notag
 \end{align}
@@
 bear a striking resemblance to \cref{eq:NLbending}.
+In fact, by carefully choosing peridynamic parameter values, the results can be made identical.
+For a rectangular beam of width \(b\) and thickness \(t\), choosing 
+\begin{equation}
+\omega(\xi) = |\xi|b ;\qquad \delta = \tau l \sqrt{3} ;\qquad \alpha = \frac{E b t^3}{54 \tau^4 l^4}\notag
+\end{equation}
+results in
+\begin{equation}
+W \approx E b \frac{t^3}{12} \frac{\kappa}{2}(\kappa+\tau^2 l^2 \kappa''), \notag
+\end{equation}
+the same result for both models.
 
@@
 \label{sec:Discretized}
-For analysis purposes, it is often useful to represent a continuum part with a discrete version. 
 Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
@@
 \end{align}
-Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(x-\xi_i)\) is ill-defined. 
+It is worth noting the similarity between this expression and a finite-difference fourth derivative of displacement, a result expected from Euler beam theory.
+This discretization requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(x-\xi_i)\) is ill-defined. 
 For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
@@
 \label{sec:NumMethod}
-Model behavior was evaluated by implementing the discretized equation of motion.
-The case of a beam simply supported at both ends was chosen for simplicity in both evaluation and comparison.
+Model behavior is evaluated by implementing the discretized equation of motion.
+The case of a beam simply supported at both ends is chosen for simplicity in both evaluation and comparison.
 Boundary conditions such as clamped supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
 
-Deformations for quasistatic loading were computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
+Deformations for quasistatic loading are computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
 %
@@
 The simplest test case for this model is a linear-elastic beam with a square profile.
-The models below were constrained to purely vertical movement of each point in order to reduce the total number of degrees of freedom, speeding evaluation and improving convergence.
 For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.

### 2014-02-24 BeamPaper.tex
changed to single column double spaced for review

@@
-\documentclass[5p,twocolumn]{elsarticle}
+%\documentclass[5p,twocolumn]{elsarticle}
+\documentclass[preprint,review,12pt]{elsarticle}
 \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
@@
 \begin{keyword}
-Peridynamics \sep non-ordinary models
+peridynamics \sep non-ordinary model \sep non-local model
 \end{keyword}
@@
 \centering
-\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{simpleBondPair.eps_tex}}
+\resizebox{0.6\linewidth}{!}{\subinputfrom{\diagrampath}{simpleBondPair.eps_tex}}
 \caption{Illustration of a bond pair model that resists angular deformation}
@@
 \centering
-\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{bondPair.eps_tex}}
+\resizebox{0.6\linewidth}{!}{\subinputfrom{\diagrampath}{bondPair.eps_tex}}
 \caption{Deformation and force vector states}
@@
 \begin{figure}[h]
-\resizebox{\linewidth}{!}{\subinputfrom{\diagrampath}{EulerBending.eps_tex}}
+\centering
+\resizebox{0.5\linewidth}{!}{\subinputfrom{\diagrampath}{EulerBending.eps_tex}}
 \caption{Euler beam moment contribution}
@@
 The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
-It is therefore unsurprising that, like Eringen's nonlocal elasticity, the peridynamic bending model fails to predict the stiffening associated with nanoscale cantilevers.
+It is therefore unsurprising that, like Eringen's nonlocal elasticity\cite{Challamel2008small}, this peridynamic bending model fails to predict the stiffening associated with nanoscale cantilevers.
 Instead, the advantage of peridynamic models is their natural handling of discontinuities.
@@
   \centering
-  \resizebox{\linewidth}{!}{\input{\plotpath/elastic_h20_g2000.pgf}}
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/elastic_h20_g2000.pgf}}
   \caption{The uniform-load elastic beam is accurately modeled with few nodes}
@@
   \centering
-  \resizebox{\linewidth}{!}{\input{\plotpath/eppu_h10_g2000.pgf}}
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/eppu_h10_g2000.pgf}}
   \caption{The elastic perfectly-plastic beam requires finer discretization}
@@
   \centering
-  \resizebox{\linewidth}{!}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
   \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
@@
   \centering
-  \resizebox{\linewidth}{!}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
   \caption{Accurately modeling residual plastic deformation also requires a small horizon}
@@
   \centering
-  \resizebox{\linewidth}{!}{\input{\plotpath/brittle_h10_n200.pgf}}
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/brittle_h10_n200.pgf}}
   \caption{A brittle beam with prescribed center displacement}

### 2014-04-16 BeamPaper.tex
Added trackchanges.sty

@@
 \usepackage[section]{placeins}
+\usepackage[inline]{trackchanges}
 
@@
 \section{Introduction}
-A goal of many mechanical engineering analyses is the prediction and description of material failure.
+\note{Re: Rev.
+I, Comment 3}\change{A goal of many mechanical engineering analyses is the prediction and description of material failure.}{James, this is just an example of how to use trackchanges, please remove this comment}
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  
 A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.
-Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.
+Various peridynamic material models capture the deformation \note{Another example, you have to go around citations} \change{behavior of 3-dimensional solid objects}{You have to stop short of citations} \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, \add{and start more after} but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.
 Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.

### 2014-04-18 response/response.tex
finished revision edits

\documentclass{article}
\usepackage[left=1.0in,right=1.0in,top=1.0in,bottom=1.0in]{geometry}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{amsmath}
%\usepackage[normalem]{ulem}
\usepackage{cancel}
\definecolor{light-gray}{gray}{0.5}

\begin{document}

\begin{center}
    {\LARGE \bf Point-by-Point Response to Reviewer's Comments} \\
     Author's Responses in {\color{red} Red}
\end{center}

%%%% First Reviewer %%%%
\section{Reviewer}
%
\subsection*{General Statement}
Let me state at the outset that this is a welcome paper adressing a problem with much educational (and perhaps practical) value. It should certainly be published after revision to address some issues (some minor, some less so).
In this paper the authors use the basic concepts of the peridynamic theory (of 3D solids) to develop and study a similar model for beams. Their approach is not one which uses the 3D peridynamic theory to look at a beam as a 3D structure but rather one where a peridynamic-like approach is developed and applied to examining the 1D theory of bending (with of course 3D considerations used and averaged across the cross-section to develop the constitutive law). This seems to me to be a good way to proceed.
%
\subsection*{Specific Comments}

\begin{enumerate}
%
   \item There is some literature on peridynamics and beams which the authors are not aware of, e.g. A displacement based framework for the micromechanics of elastic beams by G. Failla, A. Sofi and M. Zingales which is to (or has already) appeared in IJSS.
   {\color{red}
     \begin{itemize}
        \item We were unable to find the specific paper mentioned, but a search revealed interesting and relevant work by Paola et al. that is definitely worth mentioning and has been added to section 1.1
     \end{itemize}}
%
  \item The authors mention in the Introduction that the Eringen model cannot reproduce the scale stiffening observed in nanoscale beams. Does their model reproduce the correct effects? Can they compare with experiments?
   {\color{red}
     \begin{itemize}
        \item In the last paragraph of Appendix B (previously Section 3), it is noted that:
        \begin{quote}
        It is therefore unsurprising that, like Eringen's nonlocal elasticity [Challamel2008], this peridynamic bending model fails to predict the stiffening associated with nanoscale cantilevers.''
        \end{quote}
        \item More generally, this model, like Eringen's model, predicts relative softening of nanoscale beams. Its advantages lie in the lack of spatial derivatives.
     \end{itemize}}
%
  \item In section 1.2 they say that “The term peridynamic was coined by Silling in [11]...” while this is correct, Silling did much more than coin the term in that paper. He laid out the theory there for the first time. He should be given credit for more than coining a term.
  {\color{red}
     \begin{itemize}
        \item Very true! We took Silling's creation of the field for common knowledge and have corrected the first line of 1.2 to more accurately credit him.
     \end{itemize}}
%
     \item It is not clear to me how the authors use the energy $w = \alpha[1 + cos\theta]$ in their derivation of equation (2). Since equation (2) relates force states and kinematic states it must be based on some constitutive hypothesis (presumably this energy function). The authors should provide more detail on the derivation of (2) and its relation to w.
  {\color{red}
     \begin{itemize}
        \item The derivation has been added along as Appendix A.
     \end{itemize}}
%
     \item I am confused in section 2.1 when the energy suddenly becomes $w = \omega(\xi)\alpha[1 + cos \theta]$ rather than the one they had earlier $w = \alpha[1 + cos\theta]$ . Isn’t it the former (with the $\omega$) the one that is fundamental to this peridynamic-like model and shouldn’t it be introduced at the outset? Shouldn’t it be used, e.g. in the discussion leading to (2) and not $w = \alpha[1 + cos\theta]$ .
  {\color{red}
     \begin{itemize}
        \item The weighting function is now included from before equation (2) in the definition of the model.
        \end{itemize}}
%
  \item In Section 4.2 the authors say the uniformly loaded beam is simply-supported at the two ends. Surely this is not adequate for the peridynamic model? Or if it is, there should be a careful explanation of why this is so. In general the formulation of the boundary conditions is intimately tied up with the sort of theory being used. For example in the strain gradient theory of elasticity the boundary conditions are different to those of the classical theory of elasticity. Or in the Timoshenko beam theory it is not enough the say that the displacement and bending moment vanish at a support.
%
     {\color{red}
     \begin{itemize}
        \item Added significant detail to the discussion of boundary conditions.
     \end{itemize}}
%
\end{enumerate}

\section{Reviewer}
\subsection*{General Statement}

%
\subsection*{Specific Comments}

\begin{enumerate}

  \item A remarkable feature of the proposed beam model is that it consists only of a material model – the equilibrium equation is the same as for a continuum. The authors should consider highlighting this fact as compared with traditional beam theories, which rely on deriving new equilibrium equations.
%
     {\color{red}
     \begin{itemize}
        \item A line added to the second paragraph of the Introduction makes this clearer:
        \begin{quote}
        \underline{Unlike many continuum beam theories that derive new equations of motion (such as fourth} \underline{order PDE's) from the 3D elastic constitutive model, the new} \cancel{This} model is not derived from prior ordinary peridynamic models based on bond extension, but \underline{is a material model that} directly resists bending deformation \underline{while maintaining the same conservation of momentum} \underline{equation as the 3D model}.
        \end{quote}
     \end{itemize}}
%
  \item In equation (1), define u.
%
     {\color{red}
     \begin{itemize}
        \item Added to the line above equation (1)
     \end{itemize}}
%
  \item I’m not sure I understand the significance of the particular choice of weighting function in equation (6). It seems like there could be many choices that reproduce EI in the standard theory. Please clarify.
%
     {\color{red}
     \begin{itemize}
        \item Added the following sentence, which should clarify this issue.
        \begin{quote}
While any function $\omega(\xi)$ that produces a convergent integral for $m$ will reproduce an elastic Euler beam, a physically meaningful choice of $\omega$ will allow us to extend our model to certain inelastic behaviors.
        \end{quote}
     \end{itemize}}
%
  \item The relationship with Eringen’s model is interesting but a bit of a distraction, and it could safely be moved to an appendix where it would not interrupt the main development.
%
     {\color{red}
     \begin{itemize}
        \item The section has been moved to Appendix B
     \end{itemize}}
%
  \item The symbol t (not bold) is used with multiple meanings, please disambiguate.
%
     {\color{red}
     \begin{itemize}
        \item Substituted $t_\text{1D}$ and $\sigma_\text{1D}$ for the the non-bold instances of t and $\sigma$ from Eringen's work.
     \end{itemize}}
%
  \item In section 4.1, it should be stated that the model is for a particular choice of horizon, which is $\delta = 2\xi$. Also, I don’t see where $\omega$ is defined.
%
     {\color{red}
     \begin{itemize}
        \item The model leaves $\delta$ and $\omega$ undetermined. The first equations of section 3.1 (formerly 4.1) have been altered and a note added to make that clear.
        \begin{quote}
          \underline{in which $\boldsymbol{\xi}_i$ is the $i^\textnormal{th}$ bond emanating from the point $\mathbf{x}$ to each of the $n$ points within distance} \underline{ $\delta$ of point $\mathbf{x}$.}
        \end{quote}
     \end{itemize}}
%
  \item In section 4.2, the sentence “Boundary conditions... require careful treatment...” is vague. Please elaborate on how boundary conditions are implemented.
%
     {\color{red}
     \begin{itemize}
        \item Added significant detail to the discussion of boundary conditions.
     \end{itemize}}
%
  \item In section 4.3, it should be stated that the EPP model is the one discussed in section 2.2, so readers can easily find this.
%
     {\color{red}
     \begin{itemize}
        \item Reference to EPP model equation added
     \end{itemize}}
%
  \item I don’t understand why the residual displacements in Figure 9 are greater than the loaded displacements in Figure 8. Are these two different loading conditions?
%
     {\color{red}
     \begin{itemize}
        \item The residual displacements are actually a little more then 10\% of the loaded displacements, so the plots are on difference scales. Text has been added to make that clearer.
     \end{itemize}}
%
  \item Please define the material and damage model used in Figure 11; also define “node health”. Alternatively, since damage modeling within the new beam theory is sure to be an interesting and deep subject that merits careful analysis, the authors may wish to consider writing a separate paper about this.
%
     {\color{red}
     \begin{itemize}
        \item Added a short description of the brittle model to the end of section 2.2. Node health is defined in the text referencing the model, but is edited for clarity
        \begin{quote}
          This is borne out by the results in figure 11, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have \underline{never exceeded their critical angle and therefore } \underline{have} not failed.
        \end{quote}
     \end{itemize}}
%
  \item Similarly, in section 5, the authors should not refer to “the proposed damage model” since there isn’t really a discussion of a damage model in the paper.
%
     {\color{red}
     \begin{itemize}
        \item Changed the wording of the conclusion:
        \begin{quote}
          The \cancel{proposed} \underline{perfect plasticity and simple brittle} damage models successfully reproduce the impact of nonlinear \cancel{elasticity} \underline{behaviors} on deformation of a rectangular cantilever, and the framework is laid to allow application of the same models to I-beams.
        \end{quote}
     \end{itemize}}
%
\end{enumerate}

\end{document}

### 2014-04-18 BeamPaper.tex
finished revision edits

--- 2014-02-24 BeamPaper.tex
@@
 \usepackage{tikz}
-\usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage{xfrac}
@@
 \usepackage[section]{placeins}
-
+\usepackage[inline]{trackchanges}
+\usepackage{morefloats}
 \usepackage{cleveref}
@@
 	\ifstrempty{#3}{}{\langle #3 \rangle}}
+
+\newcommand\tvstate[3]{%
+	\mathbf{\underline{#1}\vphantom{\hat{\underline{#1}}}}%
+	\ifstrempty{#2}{}{[#2]}%
+	\ifstrempty{#3}{}{\langle #3 \rangle}}
+
 \newcommand\sstate[3]{%
@@
 \begin{keyword}
-peridynamics \sep non-ordinary model \sep non-local model
+peridynamics \sep non-ordinary model \sep non-local model \sep non-local beam
 \end{keyword}
@@
 This paper presents a peridynamic equivalent to an Euler-Bernoulli beam, along with a methodology for representing non-uniform cross-sections, plastic behavior, and failure.
-This model is not derived from prior ordinary peridynamic models based on bond extension, but directly resists bending deformation.
+\note{Re: Rev 2, Comm 1}
+\add{Unlike many continuum beam theories that derive new equations of motion (such as fourth order PDE's) from the 3D elastic constitutive model, the new}\remove{This} model is not derived from prior ordinary peridynamic models based on bond extension, but \add{is a material model that }directly resists bending deformation \add{while maintaining the same conservation of momentum equation as the 3D model}.
 In addition to directly modeling a beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
@@
 \Cref{sec:ModelDev} presents the state based beam model and demonstrates equivalence to classical Euler-Bernoulli beam theory in the limit of shrinking nonlocality.
-\Cref{sec:EringenCompare} demonstrates the model's relationship to Eringen's nonlocal elasticity for small peridynamic horizons.
 \Cref{sec:Numerical} demonstrates the beam model with simple numerical examples.
+\ref{sec:EringenCompare} demonstrates the model's relationship to Eringen's nonlocal elasticity for small peridynamic horizons.
 %
@@
 Because the gradients are evaluated locally, gradient models are called \textit{weakly nonlocal}.
+\note{Re: Rev 1, Comm 1}\add{Recent work by Paolo et al.}\cite{paola2013mechanically}\add{develops a displacement-based beam in which relative axial displacement, shear displacement, and rotation of non-adjacent beam segments are resisted by three kinds of nonlocal spring, whose stiffnesses can be tuned to the expected material behavior.
+With the appropriate nonlocal stiffnesses, their model reproduces the nanoscale cantilever stiffening effect.}
 
@@
 \label{sec:PDintro}
-The term \textit{peridynamic} was coined by Silling in \cite{silling2000reformulation} and alludes to the fact that the force at a point is affected by nearby material configuration.
+The term \textit{peridynamic} \note{Re: Rev 1, Comm 3} \remove{was coined by Silling in [] and} alludes to the fact that the force at a point is affected by nearby material configuration\change{.}{ and was coined by Silling to describe the new formulation of continuum mechanics he developed in } \cite{silling2000reformulation}
 In contrast to gradient models, the peridynamic model is \textit{strongly nonlocal} and casts material behavior at a point as the \textit{integral equation} 
@@
 in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
-The deformed image of the vector $\mathbf{q-x}$) is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation}. 
+The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} \note{Re: Rev 2, Comm 2}\add{for a displacement field} \(\mathbf{u}\).
 %
@@
 %
-If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \( w = \alpha [1 + \cos(\theta) ] \), we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic}.
+If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \note{Re: Rev 1, Comm 4\&5}\(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \)\add{for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in }\cite{silling2007peridynamic} \add{by taking the Fr\'echet derivative.
+For the derivation and a description of the Fr\'echet derivative see} \ref{sec:frechet}.
 %
-\begin{equation}
+\begin{align}
 \label{eq:SillingForceNO}
-\vstate{T}{}{\boldsymbol{\xi}} =\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
-\end{equation}
+\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
+%
+&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
+\end{align}
 %
@@
 \label{eq:continuousBeamw}
-w &= \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \notag\\
+w(\xi) &= \omega(\xi) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \notag\\
 &\approx \omega(\xi) \alpha\frac{\xi^2}{2}(\kappa)^2 +\mathcal{O}(\xi^4).\notag
@@
 
-\subsection{Weighting function and perfect plasticity}
+While this demonstrates the model's equivalence to a linearly-elastic Euler beam, if we keep an additional term from the Taylor series approximation of \cref{eq:beamdtheta}, we recover a slightly more complex expressions for change in angle that is demonstrated in \ref{sec:EringenCompare} to reproduce an Euler beam governed by Eringen's model of nonlocal elasticity.
+
+\subsection{Weighting function and inelasticity}
 \label{sec:WeightFunction}
 The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
+\note{Re: Rev 2, Comm 3}
+\add{While any function $\omega(\xi)$ that produces a convergent integral for $m$ will reproduce an elastic Euler beam, a physically meaningful choice of $\omega$ will allow us to extend our model to certain inelastic behaviors.}
 Consider a classical Euler-Bernoulli beam in bending with curvature \(\kappa\). 
@@
 An example for a rectangular beam is illustrated in \cref{fig:WeightProfileUniform}.
-For an I beam with height \(h_\text{beam}\), width \(w_\text{beam}\), web height \(h_\text{web}\), and web width \(w_\text{web}\), substituting the beam profile
+For an I beam with height \(h_\text{beam}\), width \(w_\text{beam}\), web height \(h_\text{web}\), and web width \(w_\text{web}\), substituting the beam profile\note{added $|\xi|$ term to weight function}
 \begin{equation}
@@
   \begin{dcases}
-    w_\text{web} & \text{if } |\xi| \leq \delta\frac{h_\text{web}}{h_\text{beam}} \\
-    w_\text{beam} & \text{if } \delta\frac{h_\text{web}}{h_\text{beam}} < |\xi| \leq \delta \\
+    |\xi| w_\text{web}& \text{if } |\xi| \leq \delta\frac{h_\text{web}}{h_\text{beam}} \\
+    |\xi| w_\text{beam} & \text{if } \delta\frac{h_\text{web}}{h_\text{beam}} < |\xi| \leq \delta \\
     0 &\text{otherwise}
@@
 %
-\[ 
+\begin{equation}
 |\vstate{T}{}{\xi}| = 
   \begin{cases}
-    \alpha \frac{\sin(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}))}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta < \theta_c\\
-    \alpha \frac{\sin(\theta_c)}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta \geq \theta_c\
+    \alpha \omega(\xi) \frac{\sin(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}))}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta < \theta_c\\
+    \alpha \omega(\xi) \frac{\sin(\theta_c)}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta \geq \theta_c\
   \end{cases}
-\]
+  \label{eq:epp_force}
+\end{equation}
 %
@@
 By keeping track of the plastic deformation \(\theta^p (\xi) = \theta-\theta_c\) of each bond-pair, and applying it as an offset, we can reproduce the hysteresis associated with elastic-perfectly-plastic deformation.
+
+\add{More simply, we can model a brittle material by setting the force to zero for bond pairs exceeding a critical angle,}
+%
+\begin{equation}
+|\vstate{T}{}{\xi}| = 
+  \begin{cases}
+    \alpha \omega(\xi) \frac{\sin(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}}))}{|\vstate{Y}{}{\xi}|} & \quad \text{if } \theta < \theta_c\\
+    0 & \quad \text{if } \theta \geq \theta_c\
+  \end{cases}
+  \label{eq:brittle_force}
+\end{equation}
+%
+\add{and additionally recording bond pairs that have exceeded their critical angle and permanently setting their influence, i.e. $\omega$, to zero.}
 %
 %
+\section{Numerical Simulation}
+\label{sec:Numerical}
+\subsection{Discretized Model}
+\label{sec:Discretized}
+Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
+\note{Re: Rev 2, Comm 6, also added $\omega(\xi_i)$ to expressions}
+%
+\begin{align}
+%\label{eq:discreteBeamw}
+w(\boldsymbol{\xi}_i) &= \omega(\boldsymbol{\xi}_i)\alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}_i},\vstate{Y}{}{-\boldsymbol{\xi}_i})) \right] \notag \\
+&\approx \omega(\boldsymbol{\xi}_i)\frac{\alpha}{2}\left(\frac{v(\mathbf{x}+\boldsymbol{\xi}_i)-2v(\mathbf{x})+v(\mathbf{x}-\boldsymbol{\xi}_i)}{\boldsymbol{\xi}_i}\right)^2 \notag
+\end{align}
+%
+\add{in which $\boldsymbol{\xi}_i$ is the $i^\textnormal{th}$ bond emanating from the point $\mathbf{x}$ to each of the $n$ points within distance $\delta$ of point $\mathbf{x}$.}
+%
+\begin{align}
+\label{eq:discretebeam}
+\alpha &= \frac{c\; \Delta x}{m} ;\; c= EI ;\; m=\sum_{i=1}^n \omega(\boldsymbol{\xi}_i)\boldsymbol{\xi}_i^2 \implies \nonumber \\
+W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\omega(\boldsymbol{\xi}_i)\left(\frac{v(\mathbf{x}+\boldsymbol{\xi}_i)-2v(\mathbf{x})+v(\mathbf{x}-\boldsymbol{\xi}_i)}{\boldsymbol{\xi}_i}\right)^2\notag
+\end{align}
+%
+Discretization of the original model results in the equation of motion
+\begin{align}
+\rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})&+\sum_i \omega(\boldsymbol{\xi}_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \left[ \frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right] \right.
+\notag \\
+& \left.
+-\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |} \right] \right\} \notag
+\end{align}
+with
+\begin{align}
+\mathbf{p}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
+\mathbf{q}_i &= -\boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}-\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
+\mathbf{r}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+2\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i).\notag
+\end{align}
+and for small displacements and rotations in a uniform beam,
+\begin{align}
+\rho(\mathbf{x})\ddot{v}(\mathbf{x}) = &f(\mathbf{x})\notag \\
++&\alpha \sum_i 2\omega(\xi_i)\left(\frac{v(\mathbf{x}-2 \boldsymbol{\xi}_i)-4v(\mathbf{x}- \boldsymbol{\xi}_i)+6v(\mathbf{x})-4v(\mathbf{x}+ \boldsymbol{\xi}_i)+v(\mathbf{x}+2 \boldsymbol{\xi}_i)}{ \boldsymbol{\xi}_i^2}\right) \notag
+\end{align}
+It is worth noting the similarity between this expression and a finite-difference fourth derivative of displacement, a result expected from Euler beam theory.
+This discretization requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(\mathbf{x}- \boldsymbol{\xi}_i)\) is ill-defined. 
+For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
+%
+\subsection{Numerical Method}
+\label{sec:NumMethod}
+Model behavior is evaluated by implementing the discretized equation of motion.
+The case of a beam simply supported at both ends is chosen for simplicity in both evaluation and comparison.
+\note{Re: Rev1, Comm 6 and Rev 2, Comm 7}\add{To implement the simply-supported condition, it was sufficient to constrain the displacement of a single node for each support.
+Additional constraints would be necessary to approximate beam theories more complex than Euler-Bernoulli.
+In a static analysis, extending the beam two horizons outside each support has no effect on the analytical solution but moves any end-condition effects outside the area of interest.}
+Boundary conditions such as clamped supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
+\add{While applying displacement constraints is straightforward, the appropriate way to apply an angle constraint or moment to a peridynamic point or collection of points is less obvious.}
+
+Deformations for quasistatic loading are computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
+\note{Re: Rev 2, Comm 10}\add{In the case of the brittle material model, the beam was loaded until a few bond pairs exceeded the critical angle.
+The most deformed bond pair was broken, and the load step repeated, continuing until total failure.}
+%
+\subsection{Results}
+\label{sec:Results}
+The simplest test case for this model is a linear-elastic beam with a square profile.
+For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.
+Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:elastic_g2000}.
+
+\begin{figure}[h]
+  \centering
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/elastic_h20_g2000.pgf}}
+  \caption{The uniform-load elastic beam is accurately modeled with few nodes}
+  \label{fig:elastic_g2000}
+\end{figure}
+
+As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
+This behavior is mimicked by the plasticity of the longest bond-pairs \note{Re: Rev 2, Comm 8}\add{described in} \cref{eq:epp_force}, producing the results shown in \cref{fig:eppu_h10_g2000}.
+To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
+\begin{figure}[h]
+  \centering
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/eppu_h10_g2000.pgf}}
+  \caption{The elastic perfectly-plastic beam requires finer discretization}
+  \label{fig:eppu_h10_g2000}
+\end{figure}
+
+A material that is plastically deformed does not return to its original state when unloaded.
+For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
+\note{Re:Rev 2, Comm 9}\add{The Abaqus model retains slightly more than} \sfrac{1}{10} \add{of its loaded displacement after being completely unloaded.}
+This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticityN,fig:ResidualPlasticityH}. 
+Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.
+
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
+  \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
+  \label{fig:ResidualPlasticityN}
+\end{figure}
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
+  \caption{Accurately modeling residual plastic deformation also requires a small horizon}
+  \label{fig:ResidualPlasticityH}
+\end{figure}
+
+It is more difficult to verify the brittle material model \note{Re: Rev 2, Comm 10\&11}\add{described by} \cref{eq:brittle_force} because brittle failure is unstable.
+When a crack begins, moment is transferred to other bond pairs, and failure progresses until every pair of bonds surrounding a node are broken, creating a hinge at that node.
+This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have \note{Re: Rev 2, Comm 10}\add{never exceeded their critical angle and therefore have }not failed.
+
+\begin{figure}[h]
+  \centering
+  \resizebox{0.5\linewidth}{!}{\input{\plotpath/brittle_h10_n200.pgf}}
+  \caption{A brittle beam with prescribed center displacement}
+  \label{fig:brittleBeam}
+\end{figure}
+
+Unlike a local model, partial failure is observed at nodes near the plastic hinge, as pairs of bonds that straddle the hinge are broken.
+
+\section{Conclusion}
+\label{sec:Conclusion}
+
+As far as we know, this the first peridynamic state based thin feature model, and results in accurate deformation results for simple beam tests.
+The \change{proposed}{perfect plasticity and simple brittle} damage models successfully reproduce the impact of nonlinear \change{elasticity}{behaviors} on deformation of a rectangular cantilever, and the framework is laid to allow application of the same models to I-beams.
+It simplifies treatment of bending in beams, and is extensible to bending in plates.
+\appendix
+\section{Fr\'echet Derivative}
+\label{sec:frechet}
+
+The derivative of a function of a state is defined by Silling in \cite{silling2007peridynamic} as follows:
+\begin{quote}
+Let $\Psi$ be a function of a state, $\Psi(\cdot):\mathcal{A}_m\rightarrow\mathcal{L}_n$.
+Suppose there exists a state-valued function denoted $\nabla\Psi\in\mathcal{A}_{m+n}$ such that for any $\vstate{A}{}{}\in\mathcal{A}_m$ and any $\Delta\vstate{A}{}{}\in\mathcal{A}_m$,
+\begin{equation}
+  \Psi(\vstate{A}{}{}+\Delta\vstate{A}{}{})=\Psi(\vstate{A}{}{})+\nabla\Psi(\vstate{A}{}{})\bullet\Delta\vstate{A}{}{}+o(||\Delta\vstate{A}{}{}||).
+\end{equation}
+Then $\Psi$ is said to be \textit{differentiable} and $\nabla\Psi$ is called the \textit{Frechet derivative} of $\Psi$.
+\end{quote}
+This is a fairly straightforward way of defining a derivative with respect to a state, and we will apply it to derive the bond force function from the bond-pair energy function
+%
+\begin{align}
+%
+\tvstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
+%
+w&=\omega\!\left(\boldsymbol{\xi}\right)\alpha\left[1+\cos\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\right]\notag \\
+%
+w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}}\right) &=
+ \omega\!\left(\boldsymbol{\xi}\right)\alpha\left[1+\cos\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\right]\notag
+\end{align}
+%
+\begin{multline}
+\nabla w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right)\bullet\Delta\tvstate{Y}{}{\boldsymbol{\xi}}= 
+w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}}\right) -w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right) \notag\\
+%
+=\omega\!\left(\boldsymbol{\xi}\right)\alpha\sin\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\!\left[\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)-\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right]
+\end{multline}
+%
+\begin{equation}
+\left[\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)-\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right] =
+\frac{\Delta\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|}\bullet \hat{\theta}\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\notag
+\end{equation}
+%
+To determine the $\hat{\theta}$ direction vector, we must construct a vector that is normal to $\tvstate{Y}{}{\boldsymbol{\xi}}$ and that is in the plane containing both $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$.
+The cross product of $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$ is a vector normal to that plane, so any vector normal to that cross product will be in the correct plane.
+Therefore, the vector $\vstate{Y}{}{\boldsymbol{\xi}}\times\left[\vstate{Y}{}{\boldsymbol{\xi}}\times\vstate{Y}{}{\boldsymbol{-\xi}}\right]$ is both normal to $\vstate{Y}{}{\boldsymbol{\xi}}$ and is in the plane containing both $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$.
+Normalizing gives us the $\hat{\theta}$ direction vector:
+%
+\begin{equation}
+\hat{\theta}\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)=
+\frac{\tvstate{Y}{}{\boldsymbol{\xi}}\times\left[\tvstate{Y}{}{\boldsymbol{\xi}}\times\tvstate{Y}{}{\boldsymbol{-\xi}}\right]}{|\tvstate{Y}{}{\boldsymbol{\xi}}||\tvstate{Y}{}{\boldsymbol{\xi}}||\tvstate{Y}{}{\boldsymbol{-\xi}}|\sin\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)}\notag
+\end{equation}
+%
+We combine all of these to get the expression for bond force found in \cref{eq:SillingForceNO}.
+\begin{align}
+%
+\tvstate{T}{}{\boldsymbol{\xi}} &=
+\omega\!\left(\boldsymbol{\xi}\right)\frac{-\alpha}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \frac{\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \times 
+\left[\frac{\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \times 
+\frac{\tvstate{Y}{}{-\boldsymbol{\xi}}}{|\tvstate{Y}{}{-\boldsymbol{\xi}}|}\right]\notag
+\end{align}
+%
+
 \section{Relation to Eringen Nonlocality}
@@
 \begin{equation}
-\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
+\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\boldsymbol{\sigma}(\mathbf{x}')dv(\mathbf{x}').\notag
 \end{equation}
 In the local limit these relationships take the form of higher-order gradients.
-Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t\) and \(\sigma\) 
+Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t_\text{1D}\) and \(\sigma_\text{1D}\) \note{Re: Rev 2, Comm 5}
 \begin{align}
-\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)t&=\sigma,\notag
+\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)t_\text{1D}&=\sigma_\text{1D},\notag
 \end{align}
 in which \(\tau^2l^2\) is a scale-based material parameter.
-For well-behaved \(t\) and \(\sigma\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
+For well-behaved \(t_\text{1D}\) and \(\sigma_\text{1D}\) and small values of \(\sigma_\text{1D}''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
 \begin{equation}
 \label{eq:NLstress}
-t=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\sigma.\notag
+t_\text{1D}=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\sigma_\text{1D}.\notag
 \end{equation}
@@
 
-\section{Numerical Simulation}
-\label{sec:Numerical}
-\subsection{Discretized Model}
-\label{sec:Discretized}
-Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
-%
-\begin{align}
-%\label{eq:discreteBeamw}
-w &= \alpha \left[1+\cos(\theta(\vstate{Y}{}{\xi},\vstate{Y}{}{\mathbf{-\xi}})) \right] \notag \\
-&\approx \frac{\alpha}{2}\left(\frac{v(x+\xi)-2v(x)+v(x-\xi)}{\xi}\right)^2 \notag
-\end{align}
-%
-\begin{align}
-\label{eq:discretebeam}
-\alpha &= \frac{c\; \Delta x}{m} ;\; c= EI ;\; m=\sum_{i=1}^n \omega(\xi_i)\xi_i^2 \implies \nonumber \\
-W&=\Delta x \sum_{i=1}^n \frac{EI}{2}\left(\frac{v(x+\xi_i)-2v(x)+v(x-\xi_i)}{\xi_i}\right)^2\notag
-\end{align}
-%
-Discretization of the original model results in the equation of motion
-\begin{align}
-\rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})&+\sum_i \omega(\xi_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \left[ \frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right] \right.
-\notag \\
-& \left.
--\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |} \right] \right\} \notag
-\end{align}
-with
-\begin{align}
-\mathbf{p}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
-\mathbf{q}_i &= -\boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}-\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
-\mathbf{r}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+2\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i).\notag
-\end{align}
-and for small displacements and rotations in a uniform beam,
-\begin{align}
-&\rho(x)\ddot{v}(x) = f(x)+\alpha \sum_i 2\omega(\xi_i)\bigg( \notag\\
-&\left. \frac{v(x-2\xi_i)-4v(x-\xi_i)+6v(x)-4v(x+\xi_i)+v(x+2\xi_i)}{\xi_i^2}\right) \notag
-\end{align}
-It is worth noting the similarity between this expression and a finite-difference fourth derivative of displacement, a result expected from Euler beam theory.
-This discretization requires that nodes be evenly spaced along the entire beam, otherwise the displacement \(v(x-\xi_i)\) is ill-defined. 
-For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
-%
-\subsection{Numerical Method}
-\label{sec:NumMethod}
-Model behavior is evaluated by implementing the discretized equation of motion.
-The case of a beam simply supported at both ends is chosen for simplicity in both evaluation and comparison.
-Boundary conditions such as clamped supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
-
-Deformations for quasistatic loading are computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
-%
-\subsection{Results}
-\label{sec:Results}
-The simplest test case for this model is a linear-elastic beam with a square profile.
-For comparison, equivalent models are created and analyzed in Abaqus 6.12 to verify simple cases.
-Even a coarse discretization successfully reproduces the elastically deformed beam shape in \cref{fig:elastic_g2000}.
-
-\begin{figure}[h]
-  \centering
-  \resizebox{0.5\linewidth}{!}{\input{\plotpath/elastic_h20_g2000.pgf}}
-  \caption{The uniform-load elastic beam is accurately modeled with few nodes}
-  \label{fig:elastic_g2000}
-\end{figure}
-
-As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
-This behavior is mimicked by the plasticity of the longest bond-pairs, producing the results shown in \cref{fig:eppu_h10_g2000}.
-To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
-\begin{figure}[h]
-  \centering
-  \resizebox{0.5\linewidth}{!}{\input{\plotpath/eppu_h10_g2000.pgf}}
-  \caption{The elastic perfectly-plastic beam requires finer discretization}
-  \label{fig:eppu_h10_g2000}
-\end{figure}
-
-A material that is plastically deformed does not return to its original state when unloaded.
-For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
-This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticityN,fig:ResidualPlasticityH}. 
-Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.
-
-%
-\begin{figure}[h]
-  \centering
-  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
-  \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
-  \label{fig:ResidualPlasticityN}
-\end{figure}
-%
-\begin{figure}[h]
-  \centering
-  \resizebox{0.5\linewidth}{!}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
-  \caption{Accurately modeling residual plastic deformation also requires a small horizon}
-  \label{fig:ResidualPlasticityH}
-\end{figure}
-
-It is more difficult to verify the brittle material model because brittle failure is unstable.
-When a crack begins, moment is transferred to other bond pairs, and failure progresses until every pair of bonds surrounding a node are broken, creating a hinge at that node.
-This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have not failed.
-
-\begin{figure}[h]
-  \centering
-  \resizebox{0.5\linewidth}{!}{\input{\plotpath/brittle_h10_n200.pgf}}
-  \caption{A brittle beam with prescribed center displacement}
-  \label{fig:brittleBeam}
-\end{figure}
-
-Unlike a local model, partial failure is observed at nodes near the plastic hinge, as pairs of bonds that straddle the hinge are broken.
-
-\section{Conclusion}
-\label{sec:Conclusion}
-
-As far as we know, this the first peridynamic state based thin feature model, and results in accurate deformation results for simple beam tests.
-The proposed damage model successfully reproduces the impact of nonlinear elasticity on deformation of a rectangular cantilever, and the framework is laid to allow application of the same model to I-beams.
-It simplifies treatment of bending in beams, and is extensible to bending in plates.
-
 \bibliographystyle{elsarticle-num}

### 2014-04-18 BeamPaper.tex
stripped out trackchanges commands

@@
 \usepackage[section]{placeins}
-\usepackage[inline]{trackchanges}
+%\usepackage[inline]{trackchanges}
 \usepackage{morefloats}
@@
 This paper presents a peridynamic equivalent to an Euler-Bernoulli beam, along with a methodology for representing non-uniform cross-sections, plastic behavior, and failure.
-\note{Re: Rev 2, Comm 1}
-\add{Unlike many continuum beam theories that derive new equations of motion (such as fourth order PDE's) from the 3D elastic constitutive model, the new}\remove{This} model is not derived from prior ordinary peridynamic models based on bond extension, but \add{is a material model that }directly resists bending deformation \add{while maintaining the same conservation of momentum equation as the 3D model}.
+Unlike many continuum beam theories that derive new equations of motion (such as fourth order PDE's) from the 3D elastic constitutive model, the new model is not derived from prior ordinary peridynamic models based on bond extension, but is a material model that directly resists bending deformation while maintaining the same conservation of momentum equation as the 3D model.
 In addition to directly modeling a beam in bending, the simple beam case lays the theoretical framework for more complex peridynamic beam, plate, and shell bending models.
@@
 Because the gradients are evaluated locally, gradient models are called \textit{weakly nonlocal}.
-\note{Re: Rev 1, Comm 1}\add{Recent work by Paolo et al.}\cite{paola2013mechanically}\add{develops a displacement-based beam in which relative axial displacement, shear displacement, and rotation of non-adjacent beam segments are resisted by three kinds of nonlocal spring, whose stiffnesses can be tuned to the expected material behavior.
-With the appropriate nonlocal stiffnesses, their model reproduces the nanoscale cantilever stiffening effect.}
+Recent work by Paolo et al.
+\cite{paola2013mechanically} develops a displacement-based beam in which relative axial displacement, shear displacement, and rotation of non-adjacent beam segments are resisted by three kinds of nonlocal spring, whose stiffnesses can be tuned to the expected material behavior.
+With the appropriate nonlocal stiffnesses, their model reproduces the nanoscale cantilever stiffening effect.
 
@@
 \label{sec:PDintro}
-The term \textit{peridynamic} \note{Re: Rev 1, Comm 3} \remove{was coined by Silling in [] and} alludes to the fact that the force at a point is affected by nearby material configuration\change{.}{ and was coined by Silling to describe the new formulation of continuum mechanics he developed in } \cite{silling2000reformulation}
+The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he developed in \cite{silling2000reformulation}.
 In contrast to gradient models, the peridynamic model is \textit{strongly nonlocal} and casts material behavior at a point as the \textit{integral equation} 
@@
 in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
-The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} \note{Re: Rev 2, Comm 2}\add{for a displacement field} \(\mathbf{u}\).
+The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} for a displacement field \(\mathbf{u}\).
 %
@@
 %
-If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \note{Re: Rev 1, Comm 4\&5}\(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \)\add{for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in }\cite{silling2007peridynamic} \add{by taking the Fr\'echet derivative.
-For the derivation and a description of the Fr\'echet derivative see} \ref{sec:frechet}.
+If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} by taking the Fr\'echet derivative.
+For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
 %
@@
 The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
-\note{Re: Rev 2, Comm 3}
-\add{While any function $\omega(\xi)$ that produces a convergent integral for $m$ will reproduce an elastic Euler beam, a physically meaningful choice of $\omega$ will allow us to extend our model to certain inelastic behaviors.}
+While any function $\omega(\xi)$ that produces a convergent integral for $m$ will reproduce an elastic Euler beam, a physically meaningful choice of $\omega$ will allow us to extend our model to certain inelastic behaviors.
 Consider a classical Euler-Bernoulli beam in bending with curvature \(\kappa\). 
@@
 An example for a rectangular beam is illustrated in \cref{fig:WeightProfileUniform}.
-For an I beam with height \(h_\text{beam}\), width \(w_\text{beam}\), web height \(h_\text{web}\), and web width \(w_\text{web}\), substituting the beam profile\note{added $|\xi|$ term to weight function}
+For an I beam with height \(h_\text{beam}\), width \(w_\text{beam}\), web height \(h_\text{web}\), and web width \(w_\text{web}\), substituting the beam profile
 \begin{equation}
@@
 
-\add{More simply, we can model a brittle material by setting the force to zero for bond pairs exceeding a critical angle,}
+More simply, we can model a brittle material by setting the force to zero for bond pairs exceeding a critical angle,
 %
@@
 %
-\add{and additionally recording bond pairs that have exceeded their critical angle and permanently setting their influence, i.e. $\omega$, to zero.}
+and additionally recording bond pairs that have exceeded their critical angle and permanently setting their influence, i.e. $\omega$, to zero.
 %
@@
 Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
-\note{Re: Rev 2, Comm 6, also added $\omega(\xi_i)$ to expressions}
 %
@@
 %
-\add{in which $\boldsymbol{\xi}_i$ is the $i^\textnormal{th}$ bond emanating from the point $\mathbf{x}$ to each of the $n$ points within distance $\delta$ of point $\mathbf{x}$.}
+in which $\boldsymbol{\xi}_i$ is the $i^\textnormal{th}$ bond emanating from the point $\mathbf{x}$ to each of the $n$ points within distance $\delta$ of point $\mathbf{x}$.
 %
@@
 The case of a beam simply supported at both ends is chosen for simplicity in both evaluation and comparison.
-\note{Re: Rev1, Comm 6 and Rev 2, Comm 7}\add{To implement the simply-supported condition, it was sufficient to constrain the displacement of a single node for each support.
+To implement the simply-supported condition, it was sufficient to constrain the displacement of a single node for each support.
 Additional constraints would be necessary to approximate beam theories more complex than Euler-Bernoulli.
-In a static analysis, extending the beam two horizons outside each support has no effect on the analytical solution but moves any end-condition effects outside the area of interest.}
+In a static analysis, extending the beam two horizons outside each support has no effect on the analytical solution but moves any end-condition effects outside the area of interest.
 Boundary conditions such as clamped supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
-\add{While applying displacement constraints is straightforward, the appropriate way to apply an angle constraint or moment to a peridynamic point or collection of points is less obvious.}
+While applying displacement constraints is straightforward, the appropriate way to apply an angle constraint or moment to a peridynamic point or collection of points is less obvious.
 
 Deformations for quasistatic loading are computed by implicitly solving the zero-acceleration discrete equation of motion with a Newton's Method solver.
-\note{Re: Rev 2, Comm 10}\add{In the case of the brittle material model, the beam was loaded until a few bond pairs exceeded the critical angle.
-The most deformed bond pair was broken, and the load step repeated, continuing until total failure.}
+In the case of the brittle material model, the beam was loaded until a few bond pairs exceeded the critical angle.
+The most deformed bond pair was broken, and the load step repeated, continuing until total failure.
 %
@@
 As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
-This behavior is mimicked by the plasticity of the longest bond-pairs \note{Re: Rev 2, Comm 8}\add{described in} \cref{eq:epp_force}, producing the results shown in \cref{fig:eppu_h10_g2000}.
+This behavior is mimicked by the plasticity of the longest bond-pairs described in \cref{eq:epp_force}, producing the results shown in \cref{fig:eppu_h10_g2000}.
 To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
@@
 For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
-\note{Re:Rev 2, Comm 9}\add{The Abaqus model retains slightly more than} \sfrac{1}{10} \add{of its loaded displacement after being completely unloaded.}
+The Abaqus model retains slightly more than \sfrac{1}{10} of its loaded displacement after being completely unloaded.
 This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticityN,fig:ResidualPlasticityH}. 
@@
 
-It is more difficult to verify the brittle material model \note{Re: Rev 2, Comm 10\&11}\add{described by} \cref{eq:brittle_force} because brittle failure is unstable.
+It is more difficult to verify the brittle material model described by \cref{eq:brittle_force} because brittle failure is unstable.
 When a crack begins, moment is transferred to other bond pairs, and failure progresses until every pair of bonds surrounding a node are broken, creating a hinge at that node.
-This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have \note{Re: Rev 2, Comm 10}\add{never exceeded their critical angle and therefore have }not failed.
+This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have never exceeded their critical angle and therefore have not failed.
 
@@
 As far as we know, this the first peridynamic state based thin feature model, and results in accurate deformation results for simple beam tests.
-The \change{proposed}{perfect plasticity and simple brittle} damage models successfully reproduce the impact of nonlinear \change{elasticity}{behaviors} on deformation of a rectangular cantilever, and the framework is laid to allow application of the same models to I-beams.
+The perfect plasticity and simple brittle damage models successfully reproduce the impact of nonlinear behaviors on deformation of a rectangular cantilever, and the framework is laid to allow application of the same models to I-beams.
 It simplifies treatment of bending in beams, and is extensible to bending in plates.
@@
 In the local limit these relationships take the form of higher-order gradients.
-Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t_\text{1D}\) and \(\sigma_\text{1D}\) \note{Re: Rev 2, Comm 5}
+Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t_\text{1D}\) and \(\sigma_\text{1D}\)
 \begin{align}
